---
title: "Final Report for Load Forecasting Competition"
subtitle: https://github.com/ayenyein-thu/LopezThu_ENV797_TSA_ForecastCompetition_S25/
author: "Aye Nyein Thu, Alex Lopez"
output: pdf_document
geometry: margin=2.54cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r, include=FALSE}
library(readxl)
library(openxlsx)
library(writexl)
library(dplyr)
library(lubridate)
library(ggplot2)
library(cowplot)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(smooth)
library(kableExtra)
library(car)
```

# Importing Data

```{r, echo=FALSE}
Demand <- read_excel(path = "./Data/Raw/load.xlsx", sheet = "Sheet1", 
                     col_names = TRUE)

Humidity <- read_excel(path = "./Data/Raw/relative_humidity.xlsx", sheet = "Sheet1", 
                       col_names = TRUE)

Temperature <- read_excel(path = "./Data/Raw/temperature.xlsx", sheet = "Sheet1", 
                          col_names = TRUE)

```

# Data Wrangling

## Demand

```{r, echo=FALSE}
# Format the hourly data set
Hourly_Demand <- Demand %>%
  pivot_longer(cols = starts_with("h"), names_to = "hour", values_to = "Hourly_demand") %>%
  mutate(Hour = as.numeric(sub("h", "", hour))) %>%
  mutate(Date = ymd(date)) %>% 
  select(Date, Hour, Hourly_demand)

summary(Hourly_Demand) # Note the 6 NA's
 
# Format the daily data set 
Daily_Demand  <- Hourly_Demand %>%
  filter(!is.na(Hourly_demand)) %>% 
  group_by(Date) %>% 
  summarise(Daily_demand = mean(Hourly_demand))

```

## Humidity

```{r, echo=FALSE}
# Format the hourly data set
Hourly_Humidity <- Humidity %>%
  mutate(Date = ymd(date), Hour = hr, 
         Hourly_humidity = rowMeans(select(.,rh_ws1:rh_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_humidity)

# Format the daily data set 
Daily_Humidity  <- Hourly_Humidity %>%
  group_by(Date) %>% 
  summarise(Daily_humidity = mean(Hourly_humidity))

```

## Temperature

```{r, echo=FALSE}
# Format the hourly data set
Hourly_Temperature <- Temperature %>%
  mutate(Date = ymd(date), Hour = hr, 
         Hourly_temp = rowMeans(select(.,t_ws1:t_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_temp)

# Format the daily data set 
Daily_Temperature  <- Hourly_Temperature %>%
  group_by(Date) %>% 
  summarise(Daily_temp = mean(Hourly_temp))

```

## Combining Daily and Hourly Data Sets
```{r, echo=FALSE}
# Combine the hourly data set
Hourly_Electricity <- Hourly_Demand %>% 
  left_join(Hourly_Humidity, by = c("Date", "Hour")) %>% 
  left_join(Hourly_Temperature, by = c("Date", "Hour"))

summary(Hourly_Electricity) # Note the 6 NA's
  
# Combine the daily data set using the simple average 
Daily_Electricity <- Daily_Demand %>% 
  left_join(Daily_Humidity, by = "Date")  %>% 
  left_join(Daily_Temperature, by = "Date")

```

## Creating Time Series Objects

```{r, echo=FALSE}
ts_Hourly_Electricity <- msts(Hourly_Electricity[,3:5], 
                             seasonal.periods = c(24,168,8766),
                             start = c(2005, 1, 1, 1)) # Added the hour

ts_Daily_Electricity <- msts(Daily_Electricity[,2:4], 
                             seasonal.periods = c(7, 365.25),
                             start = c(2005, 1, 1))
```

## Handling NA's and Outliers

```{r, echo=FALSE}
# Check missing values 
sum(is.na(ts_Hourly_Electricity))
sum(is.na(ts_Daily_Electricity))

# Check outlier by test
outlier(ts_Hourly_Electricity) 
grubbs.test(ts_Hourly_Electricity[,1]) # outlier 
grubbs.test(ts_Hourly_Electricity[,2]) # not outlier 
grubbs.test(ts_Hourly_Electricity[,3]) # not outlier 

outlier(ts_Daily_Electricity)
grubbs.test(ts_Daily_Electricity[,1]) # not outlier 
grubbs.test(ts_Daily_Electricity[,2]) # not outlier 
grubbs.test(ts_Daily_Electricity[,3]) # not outlier 

# Handle NA's and outliers for just the hourly data 
Cleaned_HDemand <- tsclean(ts_Hourly_Electricity[,1]) 
outlier(Cleaned_HDemand) 
grubbs.test(Cleaned_HDemand) # not outlier 

```

## Setting Training and Testing Windows

```{r, echo=FALSE}
n_for = 59

# Create time series for data up until February 28, 2010
ts_Daily_Electricity_Feb <- subset(ts_Daily_Electricity[,1],
                                   end = length(ts_Daily_Electricity[,1])-(365-n_for))

# Create a subset for training purposes (from January 1, 2005 to December 31, 2009)
ts_Daily_Electricity_train <- subset(ts_Daily_Electricity_Feb,
                                     end = length(ts_Daily_Electricity_Feb)-n_for)

# Create a subset for testing purposes (from January 1, 2010 to February 28, 2010)
ts_Daily_Electricity_test <- subset(ts_Daily_Electricity_Feb,
                                   start = length(ts_Daily_Electricity_Feb)-n_for+1)


# Print first 5 and last 5 rows to cross-check with figures from original Daily_Electricity df
head(ts_Daily_Electricity_train, 5)
tail(ts_Daily_Electricity_train, 5)

head(ts_Daily_Electricity_test, 5)
tail(ts_Daily_Electricity_test, 5)

# Create a subset for training purpose
n_forH = 1416 # 59 days x 24 hours 

# Create time series for data up until February 28, 2010
ts_Cleaned_HDemand_Feb <- subset(Cleaned_HDemand,
                                   end = length(Cleaned_HDemand)-(8760-n_forH))

# Create a subset for training purposes (from January 1, 2005 to December 31, 2009)
ts_Cleaned_HDemand_train <- subset(ts_Cleaned_HDemand_Feb,
                                   end = length(ts_Cleaned_HDemand_Feb)-n_forH)

# Create a subset for testing purposes (from January 1, 2010 to February 28, 2010)
ts_Cleaned_HDemand_test <- subset(ts_Cleaned_HDemand_Feb,
                                   start = length(ts_Cleaned_HDemand_Feb)-n_forH+24)

```

# 5 Best-Performing Models

## Model 1: Neural Network [223]

```{r, echo=FALSE}
# Fit NN Model
NN_fit223 <- nnetar(ts_Daily_Electricity_train, p=3, P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,2)))

NN_for223 <- forecast(NN_fit223, h=59, xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,2), h=59))

# Plot forecasting results
autoplot(NN_for223) +
  ylab("Total Electricity Demand (MW)") 

# Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for223, series="Neural Network 223",PI=FALSE)+
  ylab("Total Electricity Demand (MW)") 

# Fit and Forecast the full trained model
NN_fit223_fulldataset <- nnetar(ts_Daily_Electricity[,1], p=3, P=0,
                 xreg=fourier(ts_Daily_Electricity[,1], K=c(2,2)))

NN_for223_fulldataset <- forecast(NN_fit223_fulldataset, h=59,
                                xreg=fourier(ts_Daily_Electricity[,1], 
                                          K=c(2,2), h=59))

# Plot forecasting results
autoplot(NN_for223_fulldataset) +
  ylab("Total Electricity Demand (MW)") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for223_fulldataset, series="Neural Network Final Forecast", PI=FALSE) +
  ylab("Total Electricity Demand (MW)") 

```

## Model 2: Neural Network [2,2]

```{r, echo=FALSE}
# Fit NN Model
NN_fit22 <- nnetar(ts_Daily_Electricity_train, p=1, P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,2)))

NN_for22 <- forecast(NN_fit22, h=59, xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,2), h=59))


#Plot forecasting results
autoplot(NN_for22) +
  ylab("Total Electricity Demand (MW)") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for22, series="Neural Network 22", PI=FALSE) +
  ylab("Total Electricity Demand (MW)")

# Fit and Forecast the full trained model
NN_fit22_fulldataset <- nnetar(ts_Daily_Electricity[,1], p=1, P=0,
                 xreg=fourier(ts_Daily_Electricity[,1], K=c(2,2)))

NN_for22_fulldataset <- forecast(NN_fit22_fulldataset, h=59, 
                                 xreg=fourier(ts_Daily_Electricity[,1], 
                                          K=c(2,2), h=59))

# Plot forecasting results
autoplot(NN_for22_fulldataset) +
  ylab("Total Electricity Demand (MW)") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for22_fulldataset, series="Neural Network Final Forecast", PI=FALSE)+
  ylab("Total Electricity Demand (MW)") 

```

## Model 3: Neural Network [2,3]

```{r, echo=FALSE}
# Fit NN Model
NN_fit23 <- nnetar(ts_Daily_Electricity_train, p=1, P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,3)))

NN_for23 <- forecast(NN_fit23, h=59, xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,3), h=59))


#Plot forecasting results
autoplot(NN_for23) +
  ylab("Total Electricity Demand (MW)") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for23, series="Neural Network 23", PI=FALSE) +
  ylab("Total Electricity Demand (MW)")

# Fit and Forecast the full trained model
NN_fit23_fulldataset <- nnetar(ts_Daily_Electricity[,1], p=1, P=0,
                 xreg=fourier(ts_Daily_Electricity[,1], K=c(2,3)))

NN_for23_fulldataset <- forecast(NN_fit23_fulldataset, h=59, 
                                 xreg=fourier(ts_Daily_Electricity[,1], 
                                          K=c(2,3), h=59))

# Plot forecasting results
autoplot(NN_for23_fulldataset) +
  ylab("Total Electricity Demand (MW)") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for23_fulldataset, series="Neural Network Final Forecast", PI=FALSE) +
  ylab("Total Electricity Demand (MW)") 

```

## Model 4: Neural Network [123]

```{r, echo=FALSE}
# Fit NN Model
NN_fit123 <- nnetar(ts_Daily_Electricity_train, p=3, P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(1,2)))

NN_for123 <- forecast(NN_fit123, h=59, xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(1,2), h=59))

# Plot forecasting results
autoplot(NN_for123) +
  ylab("Total Electricity Demand (MW)") 

# Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for123, series="Neural Network 123", PI=FALSE) +
  ylab("Total Electricity Demand (MW)") 

# Fit and Forecast the full trained model
NN_fit123_fulldataset <- nnetar(ts_Daily_Electricity[,1], p=3, P=0,
                                xreg=fourier(ts_Daily_Electricity[,1], K=c(1,2)))

NN_for123_fulldataset <- forecast(NN_fit123_fulldataset, h=59,
                                xreg=fourier(ts_Daily_Electricity[,1], 
                                          K=c(1,2), h=59))

# Plot forecasting results
autoplot(NN_for123_fulldataset) +
  ylab("Total Electricity Demand (MW)") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for123_fulldataset, series="Neural Network Final Forecast", PI=FALSE) +
  ylab("Total Electricity Demand (MW)") 

# Save forecast values in the data file
NN_forecast123 <- as.data.frame(NN_for123_fulldataset$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
#write.csv(NN_forecast123, "Output/NN_forecast123.csv", row.names = FALSE)

```

## Model 5: Neural Network [121]

```{r, echo=FALSE}
# Fit NN Model
NN_fit121 <- nnetar(ts_Daily_Electricity_train, p=1, P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(1,2)))

NN_for121 <- forecast(NN_fit121, h=59, xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(1,2), h=59))

# Plot forecasting results
autoplot(NN_for121) +
  ylab("Total Electricity Demand (MW)") 

# Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for121, series="Neural Network 121", PI=FALSE) +
  ylab("Total Electricity Demand (MW)") 

# Fit and Forecast the full trained model
NN_fit121_fulldataset <- nnetar(ts_Daily_Electricity[,1], p=1, P=0,
                                xreg=fourier(ts_Daily_Electricity[,1], K=c(1,2)))

NN_for121_fulldataset <- forecast(NN_fit121_fulldataset, h=59,
                                xreg=fourier(ts_Daily_Electricity[,1], 
                                          K=c(1,2), h=59))

# Plot forecasting results
autoplot(NN_for121_fulldataset) +
  ylab("Total Electricity Demand (MW)") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for121_fulldataset, series="Neural Network Final Forecast", PI=FALSE) +
  ylab("Total Electricity Demand (MW)") 

# Save forecast values in the data file
NN_forecast121 <- as.data.frame(NN_for121_fulldataset$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
#write.csv(NN_forecast121, "Output/NN_forecast121.csv", row.names = FALSE)

```

## Model 6: Hourly

```{r, echo=FALSE}
# Fit NN Model
NN_fit121_H6 <- nnetar(ts_Cleaned_HDemand_train, p=24, P=0,
                 xreg=fourier(ts_Cleaned_HDemand_train, K=c(3,2,1)))

NN_for121_H6 <- forecast(NN_fit121_H6, h=1416, xreg=fourier(ts_Cleaned_HDemand_train, 
                                          K=c(3,2,1), h=1416))

# Plot forecasting results
autoplot(NN_for121_H6) +
  ylab("Total Electricity Demand (MW)") 

# Plot model + observed data
autoplot(ts_Cleaned_HDemand_Feb) +
  autolayer(NN_for121_H6, series="Neural Network 121H", PI=FALSE) +
  ylab("Total Electricity Demand (MW)") 


```

## Model 7

## Model 8

## Model 9

## Accuracy and Performance Testing
```{r daily model accuracy and performance, warning=FALSE, message=FALSE}
# Model 6:  NNm6
NNm6scores <- accuracy(NN_forecast121_H$mean,ts_Cleaned_HDemand_test)

# Model 7:
NNm7scores <- accuracy(NN_for22$mean,ts_Cleaned_HDemand_test)

#Model 8: 
NNm8scores <- accuracy(NN_for223$mean,ts_Cleaned_HDemand_test)

#Model 9: 
NNm9scores <- accuracy(NN_for36$mean,ts_Cleaned_HDemand_test)

# Create data frame
scores <- as.data.frame(
  rbind(NNm6scores, NNm7scores, NNm8scores, NNm9scores)
  )
row.names(scores) <- c("NNm6", "NNm7", "NNm8", "NNm9")
```

```{r}
library(forecast)
library(tidyverse)
library(Metrics) # for rmse
#install.packages("Metrics")

# Parameters to test
p_vals <- c(12, 24, 48)
P_vals <- c(0, 1)
K_vals <- list(c(2,1,1), c(3,2,1), c(3,3,1), c(4,2,2))

# Store results
results <- data.frame()

# msts object: ts_Cleaned_HDemand_train (train) and ts_Cleaned_HDemand_test (test) already defined
x_test <- ts_Cleaned_HDemand_test

for (p in p_vals) {
  for (P in P_vals) {
    for (K in K_vals) {
      cat("Testing p =", p, ", P =", P, ", K =", toString(K), "\n")
      
      try({
        # Fit the model
        fit <- nnetar(ts_Cleaned_HDemand_train, p = p, P = P,
                      xreg = fourier(ts_Cleaned_HDemand_train, K = K))
        
        # Forecast
        fcast <- forecast(fit, h = length(x_test),
                          xreg = fourier(ts_Cleaned_HDemand_train, K = K, h = length(x_test)))
        
        # Compute RMSE
        current_rmse <- rmse(as.numeric(x_test), as.numeric(fcast$mean))
        
        # Store results
        results <- rbind(results, data.frame(p = p,
                                             P = P,
                                             K = paste(K, collapse = "-"),
                                             RMSE = current_rmse))
      }, silent = TRUE)
    }
  }
}

# Sort by RMSE
results <- results %>% arrange(RMSE)
print(results)
```
