---
title: "Forecasting Competition_Part II"
author: "Alex Lopez and Aye Nyein Thu"
date: "2025-03-23"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages
```{r load packages, message=FALSE, warning=FALSE}
# Load required packages
library(readxl)
library(openxlsx)
library(writexl)
library(dplyr)
library(lubridate)
library(ggplot2)
library(cowplot)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(smooth)
library(kableExtra)

# Check working directory
getwd()
```

## Importing data sets
```{r import demand data set, results='hide', warning=FALSE, message=FALSE}
## Raw Data: Electricity Demand 
# Import the data set
Demand <- read_excel(
  path = "./Data/Raw/load.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Demand <- Demand %>%
  pivot_longer(cols = starts_with("h"), 
               names_to = "hour", 
               values_to = "Hourly_demand") %>%
  mutate(Hour = as.numeric(sub("h", "", hour))) %>%
  mutate(Date = ymd(date)) %>% 
  select(Date, Hour, Hourly_demand)

summary(Hourly_Demand) # Note the 6 missing values
 
# Format the daily data set 
Daily_Demand  <- Hourly_Demand %>%
  filter( !is.na(Hourly_demand)) %>% 
  group_by(Date) %>% 
  summarise(Daily_demand = mean(Hourly_demand)) 

## Raw Data: Relative Humidity 
# Import the data set
Humidity <- read_excel(
  path = "./Data/Raw/relative_humidity.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Humidity <- Humidity %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_humidity = rowMeans(select(.,rh_ws1:rh_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_humidity)

# Format the daily data set 
Daily_Humidity  <- Hourly_Humidity %>%
  group_by(Date) %>% 
  summarise(Daily_humidity = mean(Hourly_humidity)) 

## Raw Data: Temperature 
# Import the data set
Temperature <- read_excel(
  path = "./Data/Raw/temperature.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Temperature <- Temperature %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_temp = rowMeans(select(.,t_ws1:t_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_temp)

# Format the daily data set 
Daily_Temperature  <- Hourly_Temperature %>%
  group_by(Date) %>% 
  summarise(Daily_temp = mean(Hourly_temp)) 
```

## Data Wrangling 
```{r combining data set, results='hide', warning=FALSE, message=FALSE}
# Combine the hourly data set
Hourly_Electricity <- Hourly_Demand %>% 
  left_join(Hourly_Humidity, by = c("Date", "Hour")) %>% 
  left_join(Hourly_Temperature, by = c("Date", "Hour"))

summary(Hourly_Electricity) # Note the 6 missing values
  
# Combine the daily data set
Daily_Electricity <- Daily_Demand %>% 
  left_join(Daily_Humidity, by = "Date")  %>% 
  left_join(Daily_Temperature, by = "Date")

# Save the processed data sets in the folder 
#write.xlsx(Hourly_Electricity, "Data/Processed/Hourly_Electricity.xlsx") 
#write.xlsx(Daily_Electricity, "Data/Processed/Daily_Electricity.xlsx")
```

## Initial Data Exploration and Transforming into Time Series 
```{r initial plots, message=FALSE, warning=FALSE}}
# Plot 
ggplot(Hourly_Electricity, aes(x=Date)) +
  geom_line(aes(y=Hourly_demand), color="blue") 

ggplot(Daily_Electricity, aes(x=Date)) +
  geom_line(aes(y=Daily_demand), color="blue") 
```

```{r tranform into time series, warning=FALSE, message=FALSE}
# Transform data into time series 
ts_Hourly_Electricity <- msts(Hourly_Electricity[,3:5], 
                             seasonal.periods = c(24,168,8766),
                             start = c(2005, 1, 1, 1)) # Added the hour

ts_Daily_Electricity <- msts(Daily_Electricity[,2:4], 
                             seasonal.periods = c(7, 365.25),
                             start = c(2005, 1, 1))
```

```{r missing values and outliers, warning=FALSE, message=FALSE}
# Check missing values 
sum(is.na(ts_Hourly_Electricity))
sum(is.na(ts_Daily_Electricity))

# Replace the missing values
MV_Hourly_Electricity <- zoo::na.approx(ts_Hourly_Electricity)
sum(is.na(MV_Hourly_Electricity))

# Note: It is hard to see where the missing values is filled
autoplot(MV_Hourly_Electricity[,1], series="Wind Clean") +
  autolayer(ts_Hourly_Electricity[,1], series="Wind Raw") +
  ylab("Average Wind Speed") 

# Check outlier by test
outlier(MV_Hourly_Electricity) 
grubbs.test(MV_Hourly_Electricity[,1]) # It is outlier. 
grubbs.test(MV_Hourly_Electricity[,2]) # It is not outlier. 
grubbs.test(MV_Hourly_Electricity[,3]) # It is not outlier. 

outlier(ts_Daily_Electricity)
grubbs.test(ts_Daily_Electricity[,1]) # It is not outlier. 
grubbs.test(ts_Daily_Electricity[,2]) # It is not outlier. 
grubbs.test(ts_Daily_Electricity[,3]) # It is not outlier. 

# Clean the outliers 
Out_Hourly_Electricity <- rm.outlier(MV_Hourly_Electricity,fill=TRUE) 
outlier(Out_Hourly_Electricity) 
grubbs.test(Out_Hourly_Electricity[,1]) # It is not outlier. 
grubbs.test(Out_Hourly_Electricity[,2]) # It is not outlier. 
grubbs.test(Out_Hourly_Electricity[,3]) # It is not outlier. 
```

## Decomposition and Setting training and testing windows
```{r daily data set decompose, message=FALSE, warning=FALSE}
# Daily Data Set
# Decompose the time series
ts_Daily_Electricity_decompose <- mstl(ts_Daily_Electricity[,1])
autoplot(ts_Daily_Electricity_decompose)
```

```{r daily data set training and testing, message=FALSE, warning=FALSE}
# Create a subset for training purpose
n_for = 365
ts_Daily_Electricity_train <- subset(ts_Daily_Electricity[,1],
                                   end = length(ts_Daily_Electricity[,1])-n_for)

# Create a subset for testing purpose
ts_Daily_Electricity_test <- subset(ts_Daily_Electricity[,1],
                                   start = length(ts_Daily_Electricity[,1])-n_for)

autoplot(ts_Daily_Electricity_train)
autoplot(ts_Daily_Electricity_test)
```

## Generating Time Series Model for Daiy Data Set
### Model 1: STL + ETS
```{r Daily Model 1: STL + ETS, message=FALSE, warning=FALSE}
# Fit and forecast STL + ETS model to data
ETS_fit <-  stlf(ts_Daily_Electricity_train, h = 365)

# Plot foresting results
autoplot(ETS_fit) + ylab("Daily Electricity Demand")

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ETS_fit, series="STL + ETS",PI=FALSE) +
  ylab("Daily Electricity Demand")
```

### Model 2: ARIMA + FOURIER terms
```{r Daily Model 2: ARIMA + FOURIER, message=FALSE, warning=FALSE}
# Fit arima model with fourier terms as exogenous regressors
ARIMA_Four_fit <- auto.arima(ts_Daily_Electricity_train, 
                             seasonal=FALSE, 
                             lambda=0,
                             xreg=fourier(ts_Daily_Electricity_train,
                                          K=c(2,3)) 
                             )

ARIMA_Four_for <- forecast(ARIMA_Four_fit,
                           xreg=fourier(ts_Daily_Electricity_train,
                                        K=c(2,3),
                                        h=365),
                           h=365
                           ) 

#Plot foresting results
autoplot(ARIMA_Four_for) + ylab("Total Electricity Demand")

#Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Four_for, series="ARIMA_FOURIER",PI=FALSE) +
  ylab("Total Electricity Demand")
```

### Model 3: TBATS
```{r Daily Model 3: TBATS, message=FALSE, warning=FALSE}
# Fit TBATS Model
TBATS_fit <- tbats(ts_Daily_Electricity_train)

TBATS_for <- forecast(TBATS_fit, h=365)

#Plot foresting results
autoplot(TBATS_for) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(TBATS_for, series="TBATS",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

### Model 4: Neural Network Time Series Forecasts [2,3]
```{r Daily Model 4: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit23 <- nnetar(ts_Daily_Electricity_train,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,3)))

NN_for23 <- forecast(NN_fit23, h=365,xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,3),h=365))


#Plot foresting results
autoplot(NN_for23) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for23, series="Neural Network",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

### Model 5: Neural Network Time Series Forecasts [2,2]
```{r Daily Model 4: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit22 <- nnetar(ts_Daily_Electricity_train,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,2)))

NN_for22 <- forecast(NN_fit22, h=365,xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,2),h=365))


#Plot foresting results
autoplot(NN_for22) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for22, series="Neural Network",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

## Accuracy and Performance Testing
```{r daily model accuracy and performance, warning=FALSE, message=FALSE}
# Model 1: STL + ETS
ETS_scores <- accuracy(ETS_fit$mean,ts_Daily_Electricity_test)  

# Model 2: ARIMA + Fourier 
ARIMA_scores <- accuracy(ARIMA_Four_for$mean,ts_Daily_Electricity_test)

# Model 3:  TBATS 
TBATS_scores <- accuracy(TBATS_for$mean,ts_Daily_Electricity_test)

# Model 4:  Neural Network 23
NN_scores23 <- accuracy(NN_for23$mean,ts_Daily_Electricity_test)

# Model 5:  Neural Network 22
NN_scores22 <- accuracy(NN_for22$mean,ts_Daily_Electricity_test)

# Create data frame
scores <- as.data.frame(
  rbind(ETS_scores, ARIMA_scores, TBATS_scores, NN_scores23, NN_scores22)
  )
row.names(scores) <- c("STL+ETS", "ARIMA+Fourier","TBATS","NN23", "NN22")

# Choose model with lowest MAPE
best_model_index <- which.min(scores[,"MAPE"])
cat("The best model by MAPE is:", row.names(scores[best_model_index,])) 

# Construct tables
kbl(scores, 
      caption = "Forecast Accuracy for Daily Total Electricity Demand",
      digits = array(5,ncol(scores))) %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = "hold_position") %>%
  kable_styling(latex_options="striped", stripe_index = which.min(scores[,"MAPE"]))

# Plot 
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ETS_fit, PI=FALSE, series="STL+ETS") +
  autolayer(ARIMA_Four_for, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(TBATS_for,PI=FALSE, series="TBATS") +
  autolayer(NN_for23,PI=FALSE, series="NN23") +
  autolayer(NN_for22,PI=FALSE, series="NN22") +
  xlab("Day") + ylab("Daily Active Power") +
  guides(colour=guide_legend(title="Forecast"))

autoplot(ts_Daily_Electricity_test) +
  autolayer(ETS_fit, PI=FALSE, series="STL+ETS") +
  autolayer(ARIMA_Four_for, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(TBATS_for,PI=FALSE, series="TBATS") +
  autolayer(NN_for23,PI=FALSE, series="NN") +
  autolayer(NN_for22,PI=FALSE, series="NN22") +
  ylab("Daily Active Power") +
  guides(colour=guide_legend(title="Forecast"))
```

## Forecasting for 2011 with fulltrain data set
### Model 1: STL + ETS
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Create the time series to retain full data set
ts_Daily_Electricity_fulltrain <- ts_Daily_Electricity[,1]

## Fit and Forecast the full trained STL+ETS Model 
ETS_fit_fulltrain <- stlf(ts_Daily_Electricity_fulltrain, h = 59)

# Plot foresting results
autoplot(ETS_fit_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ETS_fit_fulltrain, series="STL + ETS Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ETS_forecast <- as.data.frame(ETS_fit_fulltrain$mean) %>%
  rename(load = 1) %>%  
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%  
  select(date, load)

# Save forecast in the output folder 
write.csv(ETS_forecast, "Output/ETS_forecast.csv", row.names = FALSE)
```

### Model 2: ARIMA + FOURIER terms
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained ARIMA + Fourier terms Model 
ARIMA_Four_fit_fulltrain <- auto.arima(ts_Daily_Electricity_fulltrain, 
                                       seasonal=FALSE, 
                                       lambda=0,
                                       xreg=fourier(ts_Daily_Electricity_fulltrain,
                                                    K=c(2,3)) 
                                       )

ARIMA_Four_for_fulltrain <- forecast(ARIMA_Four_fit_fulltrain,
                                     xreg=fourier(ts_Daily_Electricity_fulltrain,
                                                  K=c(2,3),
                                                  h=59),
                                     h=59
                                     )

# Plot foresting results
autoplot(ARIMA_Four_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Four_for_fulltrain, series="ARIMA + Fourier Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ARIMA_Four_forecast <- as.data.frame(ARIMA_Four_for_fulltrain$mean) %>%
  rename(load = 1) %>% 
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(ARIMA_Four_forecast, "Output/ARIMA_Four_forecast.csv", row.names = FALSE)

```

### Model 3: TBATS
``` {r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained TBATS Model 
TBATS_fit_fulltrain <- tbats(ts_Daily_Electricity_fulltrain)

TBATS_for_fulltrain <- forecast(TBATS_fit_fulltrain, h=59)
  
# Plot foresting results
autoplot(TBATS_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(TBATS_for_fulltrain, series="TBATS Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
TBATS_Four_forecast <- as.data.frame(TBATS_for_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder
write.csv(TBATS_Four_forecast, "Output/TBATS_Four_forecast.csv", row.names = FALSE)

```

### Model 4: Neural Network [2,3]
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 23 
NN_fit23_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,3)))

NN_for23_fulltrain <- forecast(NN_fit23_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,3),h=59))

# Plot foresting results
autoplot(NN_for23_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for23_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast23 <- as.data.frame(NN_for23_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast23, "Output/NN_forecast23.csv", row.names = FALSE)

```

### Model 5: Neural Network [2,3]
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 22
NN_fit22_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,2)))

NN_for22_fulltrain <- forecast(NN_fit22_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,2),h=59))

# Plot foresting results
autoplot(NN_for22_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for22_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast22 <- as.data.frame(NN_for22_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast22, "Output/NN_forecast22.csv", row.names = FALSE)

```
