---
title: "Final Report for Load Forecasting Competition"
subtitle: https://github.com/ayenyein-thu/LopezThu_ENV797_TSA_ForecastCompetition_S25/
author: "Aye Nyein Thu, Alex Lopez"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
geometry: margin=2.54cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(readxl)
library(openxlsx)
library(writexl)
library(dplyr)
library(lubridate)
library(ggplot2)
library(cowplot)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(smooth)
library(kableExtra)
library(car)
library(ggthemes)
```

```{r include=FALSE}
# Set theme
theme_set(
  theme_hc() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
    plot.subtitle = element_text(hjust = 0.5, size = 10, face = "plain"),
    axis.title.x = element_text(size = 10),
    axis.title.y = element_text(size = 10),
    legend.title = element_text(face = "bold", size = 10),
    legend.text = element_text(size = 9)
  ) 
)
```

\newpage
# Importing Data

```{r echo=TRUE}
Demand <- read_excel(path = "./Data/Raw/load.xlsx", sheet = "Sheet1", 
                     col_names = TRUE)

Humidity <- read_excel(path = "./Data/Raw/relative_humidity.xlsx", sheet = "Sheet1", 
                       col_names = TRUE)

Temperature <- read_excel(path = "./Data/Raw/temperature.xlsx", sheet = "Sheet1", 
                          col_names = TRUE)

```

# Data Wrangling

## Demand

```{r echo=TRUE}
# Format the hourly data set
Hourly_Demand <- Demand %>%
  pivot_longer(cols = starts_with("h"), names_to = "hour", values_to = "Hourly_demand") %>%
  mutate(Hour = as.numeric(sub("h", "", hour))) %>%
  mutate(Date = ymd(date)) %>% 
  select(Date, Hour, Hourly_demand)

#summary(Hourly_Demand) # 6 NA's
 
# Format the daily data set 
Daily_Demand  <- Hourly_Demand %>%
  filter(!is.na(Hourly_demand)) %>% 
  group_by(Date) %>% 
  summarise(Daily_demand = mean(Hourly_demand))

```

## Humidity

```{r echo=TRUE}
# Format the hourly data set
Hourly_Humidity <- Humidity %>%
  mutate(Date = ymd(date), Hour = hr, 
         Hourly_humidity = rowMeans(select(.,rh_ws1:rh_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_humidity)

# Format the daily data set 
Daily_Humidity  <- Hourly_Humidity %>%
  group_by(Date) %>% 
  summarise(Daily_humidity = mean(Hourly_humidity))

```

\newpage
## Temperature

```{r echo=TRUE}
# Format the hourly data set
Hourly_Temperature <- Temperature %>%
  mutate(Date = ymd(date), Hour = hr, 
         Hourly_temp = rowMeans(select(.,t_ws1:t_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_temp)

# Format the daily data set 
Daily_Temperature  <- Hourly_Temperature %>%
  group_by(Date) %>% 
  summarise(Daily_temp = mean(Hourly_temp))

```

## Combining Daily and Hourly Data Sets

```{r echo=TRUE}
# Combine the hourly data set
Hourly_Electricity <- Hourly_Demand %>% 
  left_join(Hourly_Humidity, by = c("Date", "Hour")) %>% 
  left_join(Hourly_Temperature, by = c("Date", "Hour"))

#summary(Hourly_Electricity) # 6 NA's
  
# Combine the daily data set using the simple average 
Daily_Electricity <- Daily_Demand %>% 
  left_join(Daily_Humidity, by = "Date")  %>% 
  left_join(Daily_Temperature, by = "Date")

```

## Creating Multi-Seasonal Time Series Objects

```{r echo=TRUE}
ts_Hourly_Electricity <- msts(Hourly_Electricity[,3:5], 
                             seasonal.periods = c(24,168,8766),
                             start = c(2005, 1, 1, 1)) # Added the hour

ts_Daily_Electricity <- msts(Daily_Electricity[,2:4], 
                             seasonal.periods = c(7, 365.25),
                             start = c(2005, 1, 1))
```

## Handling NA's and Outliers

```{r echo=TRUE}
# Check missing values 
#sum(is.na(ts_Hourly_Electricity))
#sum(is.na(ts_Daily_Electricity))

# Check outlier by test
#outlier(ts_Hourly_Electricity) 
#grubbs.test(ts_Hourly_Electricity[,1]) # outlier 
#grubbs.test(ts_Hourly_Electricity[,2]) # not outlier 
#grubbs.test(ts_Hourly_Electricity[,3]) # not outlier 

#outlier(ts_Daily_Electricity)
#grubbs.test(ts_Daily_Electricity[,1]) # not outlier 
#grubbs.test(ts_Daily_Electricity[,2]) # not outlier 
#grubbs.test(ts_Daily_Electricity[,3]) # not outlier 

# Handle NA's and outliers for just the hourly data 
ts_Hourly_Demand_clean <- tsclean(ts_Hourly_Electricity[,1]) 
#outlier(ts_Hourly_Demand_clean) 
#grubbs.test(ts_Hourly_Demand_clean) # not outlier 

```

## Setting Training and Testing Windows

```{r echo=TRUE}
# DAILY
n_for = 59 #days for January and February

# Create time series for data up until February 28, 2010
ts_Daily_Electricity_Feb <- subset(ts_Daily_Electricity[,1],
                                   end = length(ts_Daily_Electricity[,1])-(365-n_for))

# Create a subset for training purposes (from January 1, 2005 to December 31, 2009)
ts_Daily_Electricity_train <- subset(ts_Daily_Electricity_Feb,
                                     end = length(ts_Daily_Electricity_Feb)-n_for)

# Create a subset for testing purposes (from January 1, 2010 to February 28, 2010)
ts_Daily_Electricity_test <- subset(ts_Daily_Electricity_Feb,
                                   start = length(ts_Daily_Electricity_Feb)-n_for+1)


# Print first 5 and last 5 rows to cross-check with original Daily_Electricity df
#head(ts_Daily_Electricity_train, 5)
#tail(ts_Daily_Electricity_train, 5)

#head(ts_Daily_Electricity_test, 5)
#tail(ts_Daily_Electricity_test, 5)

# HOURLY
n_forH = 1416 # 59 days x 24 hours 

# Create time series for data up until February 28, 2010
ts_Hourly_Demand_Feb <- subset(ts_Hourly_Demand_clean,
                                   end = length(ts_Hourly_Demand_clean)-(8760-n_forH))

# Create a subset for training purposes (from January 1, 2005 to December 31, 2009)
ts_Hourly_Demand_train <- subset(ts_Hourly_Demand_Feb,
                                   end = length(ts_Hourly_Demand_Feb)-n_forH)

# Create a subset for testing purposes (from January 1, 2010 to February 28, 2010)
ts_Hourly_Demand_test <- subset(ts_Hourly_Demand_Feb,
                                   start = length(ts_Hourly_Demand_Feb)-n_forH+24)

```

# 5 Best-Performing Models

## Model 1: Neural Network with Hourly Data [p=24, P=0, K=c(1,1,1)]

```{r echo=TRUE}
# Fit NN Model
model1_fit <- nnetar(ts_Hourly_Demand_train, p=24, P=0,
                 xreg=fourier(ts_Hourly_Demand_train, K=c(1,1,1)))

model1_forecast <- forecast(model1_fit, h=1416, xreg=fourier(ts_Hourly_Demand_train, 
                                          K=c(1,1,1), h=1416))

# Fit and forecast with full data
model1_fit_full <- nnetar(ts_Hourly_Demand_clean, p=24, P=0,
                                xreg=fourier(ts_Hourly_Demand_clean, K=c(1,1,1)))

model1_forecast_full <- forecast(model1_fit_full, h=1416,                     
                                 xreg=fourier(ts_Hourly_Demand_clean, 
                                          K=c(1,1,1), h=1416))

# Save forecast values
model1 <- as.data.frame(model1_forecast_full$mean) %>%
  rename(load_hourly = 1) %>%
  mutate(datetime = seq.POSIXt(from = as.POSIXct("2011-01-01 00:00:00"),
                               by = "hour", 
                               length.out = n())) %>%
  mutate(date = as.Date(datetime)) %>%
  group_by(date) %>%
  summarise(load = round(mean(load_hourly)), .groups = "drop") %>%
  select(date, load)

# Remove last row (value for March 1, 2011)
model1 <- model1[-nrow(model1), ]
```

## Model 2: Neural Network with Hourly Data [p=24, P=0, K=c(1,2,1)]

```{r echo=TRUE}
# Fit NN Model
model2_fit <- nnetar(ts_Hourly_Demand_train, p=24, P=0,
                 xreg=fourier(ts_Hourly_Demand_train, K=c(1,2,1)))

model2_forecast <- forecast(model2_fit, h=1416, xreg=fourier(ts_Hourly_Demand_train, 
                                          K=c(1,2,1), h=1416))

# Fit and forecast with full data
model2_fit_full <- nnetar(ts_Hourly_Demand_clean, p=24, P=0,
                                xreg=fourier(ts_Hourly_Demand_clean, K=c(1,2,1)))

model2_forecast_full <- forecast(model2_fit_full, h=1416,                     
                                 xreg=fourier(ts_Hourly_Demand_clean, 
                                          K=c(1,2,1), h=1416))

# Save forecast values
model2 <- as.data.frame(model2_forecast_full$mean) %>%
  rename(load_hourly = 1) %>%
  mutate(datetime = seq.POSIXt(from = as.POSIXct("2011-01-01 00:00:00"),
                               by = "hour", 
                               length.out = n())) %>%
  mutate(date = as.Date(datetime)) %>%
  group_by(date) %>%
  summarise(load = round(mean(load_hourly)), .groups = "drop") %>%
  select(date, load)

#remove last row (value for March 1, 2011)
model2 <- model2[-nrow(model2), ]
```

## Model 3: Neural Network with Daily Data [p=3, P=0, K=c(2,2)]

```{r echo=TRUE}
# Fit NN Model
model3_fit <- nnetar(ts_Daily_Electricity_train, p=3, P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,2)))

model3_forecast <- forecast(model3_fit, h=59, xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,2), h=59))

# Fit and forecast with full data
model3_fit_full <- nnetar(ts_Daily_Electricity[,1], p=3, P=0,
                 xreg=fourier(ts_Daily_Electricity[,1], K=c(2,2)))

model3_forecast_full <- forecast(model3_fit_full, h=59,
                                xreg=fourier(ts_Daily_Electricity[,1], 
                                          K=c(2,2), h=59))

# Save forecast values
model3 <- as.data.frame(model3_forecast_full$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

```

## Model 4: Neural Network with Daily Data [p=1, P=0, K=c(2,2)]

```{r echo=TRUE}
# Fit NN Model
model4_fit <- nnetar(ts_Daily_Electricity_train, p=1, P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,2)))

model4_forecast <- forecast(model4_fit, h=59, xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,2), h=59))

# Fit and forecast with full data
model4_fit_full <- nnetar(ts_Daily_Electricity[,1], p=1, P=0,
                 xreg=fourier(ts_Daily_Electricity[,1], K=c(2,2)))

model4_forecast_full <- forecast(model4_fit_full, h=59,
                                xreg=fourier(ts_Daily_Electricity[,1], 
                                          K=c(2,2), h=59))

# Save forecast values
model4 <- as.data.frame(model4_forecast_full$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

```

## Model 5: Neural Network with Daily Data [p=1, P=0, K=c(1,2)]

```{r echo=TRUE}
# Fit NN Model
model5_fit <- nnetar(ts_Daily_Electricity_train, p=1, P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(1,2)))

model5_forecast <- forecast(model5_fit, h=59, xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(1,2), h=59))

# Fit and forecast with full data
model5_fit_full <- nnetar(ts_Daily_Electricity[,1], p=1, P=0,
                 xreg=fourier(ts_Daily_Electricity[,1], K=c(1,2)))

model5_forecast_full <- forecast(model5_fit_full, h=59,
                                xreg=fourier(ts_Daily_Electricity[,1], 
                                          K=c(1,2), h=59))

# Save forecast values
model5 <- as.data.frame(model5_forecast_full$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load) 

```

\newpage
# Accuracy Results (vs Validation Set)

```{r echo=TRUE}
# Model 1
model1_scores <- accuracy(model1_forecast$mean, ts_Hourly_Demand_test)  

# Model 2
model2_scores <- accuracy(model2_forecast$mean, ts_Hourly_Demand_test)

# Model 3 
model3_scores <- accuracy(model3_forecast$mean, ts_Daily_Electricity_test)

# Model 4
model4_scores <- accuracy(model4_forecast$mean, ts_Daily_Electricity_test)

# Model 5
model5_scores <- accuracy(model5_forecast$mean, ts_Daily_Electricity_test)

# Create data frame
scores <- as.data.frame(
  rbind(model1_scores, model2_scores, model3_scores, model4_scores, model5_scores)
  )
row.names(scores) <- c("Model 1", "Model 2","Model 3","Model 4", "Model 5")

```
```{r echo=FALSE}
# Construct table
kbl(scores, 
      caption = "Forecast Accuracy for Load Using Validation Data Set",
      digits = array(5,ncol(scores))) %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = "hold_position") %>%
  kable_styling(latex_options="striped")
```

\newpage
# Model Comparisons (Plots)

## Training and Validation Sets

```{r, echo=FALSE, fig.height=6, fig.width=10, message=FALSE, warning=FALSE}
autoplot(ts_Daily_Electricity_test) +
  ggtitle("Model Comparisons using Daily Data") +
  #autolayer(model1_forecast, PI=FALSE, series="Model 1") +
  #autolayer(model2_forecast, PI=FALSE, series="Model 2") +
  autolayer(model3_forecast, PI=FALSE, series="Model 3") +
  autolayer(model4_forecast, PI=FALSE, series="Model 4") +
  autolayer(model5_forecast, PI=FALSE, series="Model 5") +
  ylab("Demand (MW)") +
  guides(colour=guide_legend(title="Forecast"))

```


```{r, echo=FALSE, fig.height=6, fig.width=10, message=FALSE, warning=FALSE}
autoplot(ts_Hourly_Demand_test) +
  ggtitle("Model Comparisons using Hourly Data") +
  autolayer(model1_forecast, PI=FALSE, series="Model 1") +
  autolayer(model2_forecast, PI=FALSE, series="Model 2") +
  #autolayer(model3_forecast, PI=FALSE, series="Model 3") +
  #autolayer(model4_forecast, PI=FALSE, series="Model 4") +
  #autolayer(model5_forecast, PI=FALSE, series="Model 5") +
  ylab("Demand (MW)") +
  guides(colour=guide_legend(title="Forecast"))

```

## 2011 Forecasts with Full Data Set

```{r, fig.height=6, fig.width=10, echo=FALSE, message=FALSE, warning=FALSE}
ts_model1 <- ts(model1$load, start = c(2011, 1), frequency = 365)
ts_model2 <- ts(model2$load, start = c(2011,1), frequency = 365)

autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ts_model1, PI=FALSE, series="Model 1") +
  autolayer(ts_model2, PI=FALSE, series="Model 2") +
  autolayer(model3_forecast_full, PI=FALSE, series="Model 3") +
  autolayer(model4_forecast_full, PI=FALSE, series="Model 4") +
  autolayer(model5_forecast_full, PI=FALSE, series="Model 5") +
  guides(colour=guide_legend(title="Forecast")) +
  labs(
    title = "Forecasts for January and February 2011 using Daily Data",
    subtitle = "(After Finding Daily Averages for Hourly Forecasts)",
    x = "Time",
    y = "Demand (MW)"
  )

```

```{r, fig.height=6, fig.width=10, echo=FALSE, message=FALSE, warning=FALSE}
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ts_model1, PI=FALSE, series="Model 1") +
  autolayer(ts_model2, PI=FALSE, series="Model 2") +
  autolayer(model3_forecast_full, PI=FALSE, series="Model 3") +
  autolayer(model4_forecast_full, PI=FALSE, series="Model 4") +
  autolayer(model5_forecast_full, PI=FALSE, series="Model 5") +
  guides(colour=guide_legend(title="Forecast")) +
  labs(
    title = "Forecasts for January and February 2011 using Daily Data",
    subtitle = "(After Finding Daily Averages for Hourly Forecasts)",
    x = "Time",
    y = "Demand (MW)"
  ) +
  xlim(c(2011 + 0/365, 2011 + 58/365))

```
