---
title: "Code Testing"
author: "Aye Nyein Thu"
date: "2025-03-23"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, message=FALSE, warning=FALSE}
# Load required packages
library(readxl)
library(openxlsx)
library(writexl)
library(dplyr)
library(lubridate)
library(ggplot2)
library(cowplot)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(smooth)
library(kableExtra)

# Check working directory
getwd()
```


```{r import demand data set, results='hide', warning=FALSE, message=FALSE}
## Raw Data: Electricity Demand 
# Import the data set
Demand <- read_excel(
  path = "./Data/Raw/load.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Demand <- Demand %>%
  pivot_longer(cols = starts_with("h"), 
               names_to = "hour", 
               values_to = "Hourly_demand") %>%
  mutate(Hour = as.numeric(sub("h", "", hour))) %>%
  mutate(Date = ymd(date)) %>% 
  mutate(Year = year(date), 
         Month = month(Date), 
         Day = day(Date)) %>% 
  select(Date, Year, Month, Day, Hour, Hourly_demand)

summary(Hourly_Demand) # Note the 6 missing values
 
# Format the daily data set 
Daily_Demand  <- Hourly_Demand %>%
  filter( !is.na(Hourly_demand)) %>% 
  group_by(Date,Year,Month,Day) %>% 
  summarise(Daily_demand = mean(Hourly_demand)) 

## Raw Data: Relative Humidity 
# Import the data set
Humidity <- read_excel(
  path = "./Data/Raw/relative_humidity.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Humidity <- Humidity %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_humidity = rowMeans(select(.,rh_ws1:rh_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_humidity)

# Format the daily data set 
Daily_Humidity  <- Hourly_Humidity %>%
  group_by(Date) %>% 
  summarise(Daily_humidity = mean(Hourly_humidity)) 

## Raw Data: Temperature 

# Import the data set
Temperature <- read_excel(
  path = "./Data/Raw/temperature.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Temperature <- Temperature %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_temp = rowMeans(select(.,t_ws1:t_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_temp)

# Format the daily data set 
Daily_Temperature  <- Hourly_Temperature %>%
  group_by(Date) %>% 
  summarise(Daily_temp = mean(Hourly_temp)) 
```

```{r import demand data set, results='hide', warning=FALSE, message=FALSE}
## Raw Data: Electricity Demand 
# Import the data set
Demand <- read_excel(
  path = "./Data/Raw/load.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Demand <- Demand %>%
  pivot_longer(cols = starts_with("h"), 
               names_to = "hour", 
               values_to = "Hourly_demand") %>%
  mutate(Hour = as.numeric(sub("h", "", hour))) %>%
  mutate(Date = ymd(date)) %>% 
  select(Date, Hour, Hourly_demand)

summary(Hourly_Demand) # Note the 6 missing values
 
# Format the daily data set 
Daily_Demand  <- Hourly_Demand %>%
  filter( !is.na(Hourly_demand)) %>% 
  group_by(Date) %>% 
  summarise(Daily_demand = mean(Hourly_demand)) 

## Raw Data: Relative Humidity 
# Import the data set
Humidity <- read_excel(
  path = "./Data/Raw/relative_humidity.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Humidity <- Humidity %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_humidity = rowMeans(select(.,rh_ws1:rh_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_humidity)

# Format the daily data set 
Daily_Humidity  <- Hourly_Humidity %>%
  group_by(Date) %>% 
  summarise(Daily_humidity = mean(Hourly_humidity)) 

## Raw Data: Temperature 
# Import the data set
Temperature <- read_excel(
  path = "./Data/Raw/temperature.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Temperature <- Temperature %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_temp = rowMeans(select(.,t_ws1:t_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_temp)

# Format the daily data set 
Daily_Temperature  <- Hourly_Temperature %>%
  group_by(Date) %>% 
  summarise(Daily_temp = mean(Hourly_temp)) 
```
```


```{r combing data set, results='hide', warning=FALSE, message=FALSE}
# Combine the hourly data set
Hourly_Electricity <- Hourly_Demand %>% 
  left_join(Hourly_Humidity, by = c("Date", "Hour")) %>% 
  left_join(Hourly_Temperature, by = c("Date", "Hour"))

summary(Hourly_Electricity) # Note the 6 missing values
  
# Combine the daily data set
Daily_Electricity <- Daily_Demand %>% 
  left_join(Daily_Humidity, by = "Date")  %>% 
  left_join(Daily_Temperature, by = "Date")

# Save the processed data sets in the folder 
write.xlsx(Hourly_Electricity, "Data/Processed/Hourly_Electricity.xlsx") 
write.xlsx(Daily_Electricity, "Data/Processed/Daily_Electricity.xlsx")
```

```{r transform data into time series}
# Plot 
ggplot(Daily_Electricity, aes(x=Date)) +
  geom_line(aes(y=Daily_demand), color="blue") 
```


