---
title: "Forecasting Competition_Part II"
author: "Alex Lopez and Aye Nyein Thu"
date: "2025-03-23"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages
```{r load packages, message=FALSE, warning=FALSE}
# Load required packages
library(readxl)
library(openxlsx)
library(writexl)
library(dplyr)
library(lubridate)
library(ggplot2)
library(cowplot)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(smooth)
library(kableExtra)
library(car)

# Check working directory
getwd()
```

## Importing data sets
```{r import demand data set, results='hide', warning=FALSE, message=FALSE}
## Raw Data: Electricity Demand 
# Import the data set
Demand <- read_excel(
  path = "./Data/Raw/load.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Demand <- Demand %>%
  pivot_longer(cols = starts_with("h"), 
               names_to = "hour", 
               values_to = "Hourly_demand") %>%
  mutate(Hour = as.numeric(sub("h", "", hour))) %>%
  mutate(Date = ymd(date)) %>% 
  select(Date, Hour, Hourly_demand)

summary(Hourly_Demand) # Note the 6 missing values
 
# Format the daily data set 
Daily_Demand  <- Hourly_Demand %>%
  filter( !is.na(Hourly_demand)) %>% 
  group_by(Date) %>% 
  summarise(Daily_demand = mean(Hourly_demand)) 

## Raw Data: Relative Humidity 
# Import the data set
Humidity <- read_excel(
  path = "./Data/Raw/relative_humidity.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Humidity <- Humidity %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_humidity = rowMeans(select(.,rh_ws1:rh_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_humidity)

# Format the daily data set 
Daily_Humidity  <- Hourly_Humidity %>%
  group_by(Date) %>% 
  summarise(Daily_humidity = mean(Hourly_humidity)) 

## Raw Data: Temperature 
# Import the data set
Temperature <- read_excel(
  path = "./Data/Raw/temperature.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Temperature <- Temperature %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_temp = rowMeans(select(.,t_ws1:t_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_temp)

# Format the daily data set 
Daily_Temperature  <- Hourly_Temperature %>%
  group_by(Date) %>% 
  summarise(Daily_temp = mean(Hourly_temp)) 
```

## Data Wrangling 
```{r combining data set, results='hide', warning=FALSE, message=FALSE}
# Combine the hourly data set
Hourly_Electricity <- Hourly_Demand %>% 
  left_join(Hourly_Humidity, by = c("Date", "Hour")) %>% 
  left_join(Hourly_Temperature, by = c("Date", "Hour"))

summary(Hourly_Electricity) # Note the 6 missing values
  
# Combine the daily data set using the simple average 
Daily_Electricity <- Daily_Demand %>% 
  left_join(Daily_Humidity, by = "Date")  %>% 
  left_join(Daily_Temperature, by = "Date")
  
# Save the processed data sets in the folder 
#write.xlsx(Hourly_Electricity, "Data/Processed/Hourly_Electricity.xlsx") 
#write.xlsx(Daily_Electricity, "Data/Processed/Daily_Electricity.xlsx")
```

## Transforming into Time Series 
```{r tranform into time series, warning=FALSE, message=FALSE}
# Transform data into time series 
ts_Hourly_Electricity <- msts(Hourly_Electricity[,3:5], 
                             seasonal.periods = c(24,168,8766),
                             start = c(2005, 1, 1, 1)) # Added the hour

ts_Daily_Electricity <- msts(Daily_Electricity[,2:4], 
                             seasonal.periods = c(7, 365.25),
                             start = c(2005, 1, 1))
```

## Handling missing values and outliers
```{r missing values and outliers, warning=FALSE, message=FALSE}
# Check missing values 
sum(is.na(ts_Hourly_Electricity))
sum(is.na(ts_Daily_Electricity))

# Check outlier by test
outlier(ts_Hourly_Electricity) 
grubbs.test(ts_Hourly_Electricity[,1]) # It is outlier. 
grubbs.test(ts_Hourly_Electricity[,2]) # It is not outlier. 
grubbs.test(ts_Hourly_Electricity[,3]) # It is not outlier. 

outlier(ts_Daily_Electricity)
grubbs.test(ts_Daily_Electricity[,1]) # It is not outlier. 
grubbs.test(ts_Daily_Electricity[,2]) # It is not outlier. 
grubbs.test(ts_Daily_Electricity[,3]) # It is not outlier. 

# Handle missing values and outliers for the hourly data 
Cleaned_HDemand <- tsclean(ts_Hourly_Electricity[,1]) 
outlier(Cleaned_HDemand) 
grubbs.test(Cleaned_HDemand) # It is not outlier. 

autoplot(ts_Hourly_Electricity[,1], series="Raw Data") +
  autolayer(Cleaned_HDemand, series="Cleaned Data") +
  ylab("Hourly Electricity") # Only two data points are corrected. 
```

## Daily Demand 
### Decomposition and Setting training and testing windows
```{r daily data set decompose, message=FALSE, warning=FALSE}
# Daily Data Set
# Decompose the time series
ts_Daily_Electricity_decompose <- mstl(ts_Daily_Electricity[,1])
autoplot(ts_Daily_Electricity_decompose)
```

```{r daily data set training and testing, message=FALSE, warning=FALSE}
n_for = 59

# Create time series for only Feb 2010 
ts_Daily_Electricity_Feb <- subset(ts_Daily_Electricity[,1],
                                   end = length(ts_Daily_Electricity[,1])-(365-n_for))

# Create a subset for training purpose
ts_Daily_Electricity_train <- subset(ts_Daily_Electricity_Feb,
                                   end = length(ts_Daily_Electricity_Feb)-n_for)

# Create a subset for testing purpose
ts_Daily_Electricity_test <- subset(ts_Daily_Electricity_Feb,
                                   start = length(ts_Daily_Electricity_Feb)-n_for+1)

autoplot(ts_Daily_Electricity_train)
autoplot(ts_Daily_Electricity_test)

# Print the first and last 5 rows to check 
head(ts_Daily_Electricity_train, 5)
tail(ts_Daily_Electricity_train, 5)

head(ts_Daily_Electricity_test, 5)
tail(ts_Daily_Electricity_test, 5)
```

### Generating Time Series Model for Daiy Data Set

#### Model 4: Neural Network Time Series Forecasts [2,3]
```{r Daily Model 4: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit23 <- nnetar(ts_Daily_Electricity_train,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,3)))

NN_for23 <- forecast(NN_fit23, h=59,xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,3),h=59))


#Plot foresting results
autoplot(NN_for23) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for23, series="Neural Network 23",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

#### Model 5: Neural Network Time Series Forecasts [2,2]
```{r Daily Model 5: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit22 <- nnetar(ts_Daily_Electricity_train,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,2)))

NN_for22 <- forecast(NN_fit22, h=59,xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,2),h=59))


#Plot foresting results
autoplot(NN_for22) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for22, series="Neural Network 22",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

#### Model 10: Neural Network Time Series Forecasts [223]
```{r Daily Model 10: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit223 <- nnetar(ts_Daily_Electricity_train,
                 p=3,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,2)))

NN_for223 <- forecast(NN_fit223, h=59,xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,2),h=59))


#Plot foresting results
autoplot(NN_for223) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for223, series="Neural Network 223",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

#Model 11
```{r Daily Model 11: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit36 <- nnetar(ts_Daily_Electricity_train,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,2)))

NN_for36 <- forecast(NN_fit36, h=59, xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,2), h=59))


#Plot foresting results
autoplot(NN_for36) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for36, series="Neural Network 36",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

## Accuracy and Performance Testing
```{r daily model accuracy and performance, warning=FALSE, message=FALSE}
# Model 4:  Neural Network 23
NN_scores23 <- accuracy(NN_for23$mean,ts_Daily_Electricity_test)

# Model 5:  Neural Network 22
NN_scores22 <- accuracy(NN_for22$mean,ts_Daily_Electricity_test)

#Model 10: NN 223
NN_scores223 <- accuracy(NN_for223$mean,ts_Daily_Electricity_test)

#Model 11: NN 36
NN_scores36 <- accuracy(NN_for36$mean,ts_Daily_Electricity_test)

# Create data frame
scores <- as.data.frame(
  rbind(NN_scores23, NN_scores22, NN_scores223, NN_scores36)
  )
row.names(scores) <- c("NN23", "NN22", "NN223", "NN36")

# Choose model with lowest MAPE
best_model_index <- which.min(scores[,"MAPE"])
cat("The best model by MAPE is:", row.names(scores[best_model_index,])) 

# Construct tables
kbl(scores, 
      caption = "Forecast Accuracy for Daily Total Electricity Demand",
      digits = array(5,ncol(scores))) %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = "hold_position") %>%
  kable_styling(latex_options="striped", stripe_index = which.min(scores[,"MAPE"]))

# Plot 
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ETS_fit, PI=FALSE, series="STL+ETS") +
  autolayer(ARIMA_Four_for, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(TBATS_for,PI=FALSE, series="TBATS") +
  autolayer(NN_for23,PI=FALSE, series="NN23") +
  autolayer(NN_for22,PI=FALSE, series="NN22") +
  autolayer(ARIMA_Fourexo_for, PI=FALSE, series="ARIMA + Fourier + TempHum") +
  autolayer(ARIMA_Fourexo_forT, PI=FALSE, series="ARIMA + Fourier + Temp") + 
  autolayer(NNexo_for22,PI=FALSE, series="NN22 + Exo") + 
  autolayer(NNexo_for23,PI=FALSE, series="NN23 + Exo") + 
  autolayer(NN_for223,PI=FALSE, series="NN223 + Exo") + 
  xlab("Day") + ylab("Daily Electricity Deamand") +
  guides(colour=guide_legend(title="Forecast"))

autoplot(ts_Daily_Electricity_test) +
  autolayer(ETS_fit, PI=FALSE, series="STL+ETS") +
  autolayer(ARIMA_Four_for, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(TBATS_for,PI=FALSE, series="TBATS") +
  autolayer(NN_for23,PI=FALSE, series="NN23") +
  autolayer(NN_for22,PI=FALSE, series="NN22") +
  autolayer(ARIMA_Fourexo_for, PI=FALSE, series="ARIMA + Fourier + TempHum") +
  autolayer(ARIMA_Fourexo_forT, PI=FALSE, series="ARIMA + Fourier + Temp") +
  autolayer(NNexo_for22,PI=FALSE, series="NN22 + Exo") +
  autolayer(NNexo_for23,PI=FALSE, series="NN23 + Exo") +
  autolayer(NN_for223,PI=FALSE, series="NN223") +
  ylab("Daily Electricity Deamand") +
  guides(colour=guide_legend(title="Forecast"))
```

## Forecasting for 2011 with fulltrain data set
```{r create full train time series, message=FALSE, warning=}
# Create the time series to retain full data set
ts_Daily_Electricity_fulltrain <- ts_Daily_Electricity[,1]
```

### Model 1: STL + ETS
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained STL+ETS Model 
ETS_fit_fulltrain <- stlf(ts_Daily_Electricity_fulltrain, h = 59)

# Plot foresting results
autoplot(ETS_fit_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ETS_fit_fulltrain, series="STL + ETS Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ETS_forecast <- as.data.frame(ETS_fit_fulltrain$mean) %>%
  rename(load = 1) %>%  
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%  
  select(date, load)

# Save forecast in the output folder 
write.csv(ETS_forecast, "Output/ETS_forecast.csv", row.names = FALSE)
```

### Model 2: ARIMA + FOURIER terms
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained ARIMA + Fourier terms Model 
ARIMA_Four_fit_fulltrain <- auto.arima(ts_Daily_Electricity_fulltrain, 
                                       seasonal=FALSE, 
                                       lambda=0,
                                       xreg=fourier(ts_Daily_Electricity_fulltrain,
                                                    K=c(2,3)) 
                                       )

ARIMA_Four_for_fulltrain <- forecast(ARIMA_Four_fit_fulltrain,
                                     xreg=fourier(ts_Daily_Electricity_fulltrain,
                                                  K=c(2,3),
                                                  h=59),
                                     h=59
                                     )

# Plot foresting results
autoplot(ARIMA_Four_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Four_for_fulltrain, series="ARIMA + Fourier Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ARIMA_Four_forecast <- as.data.frame(ARIMA_Four_for_fulltrain$mean) %>%
  rename(load = 1) %>% 
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(ARIMA_Four_forecast, "Output/ARIMA_Four_forecast.csv", row.names = FALSE)
```

### Model 3: TBATS
``` {r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained TBATS Model 
TBATS_fit_fulltrain <- tbats(ts_Daily_Electricity_fulltrain)

TBATS_for_fulltrain <- forecast(TBATS_fit_fulltrain, h=59)
  
# Plot foresting results
autoplot(TBATS_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(TBATS_for_fulltrain, series="TBATS Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
TBATS_Four_forecast <- as.data.frame(TBATS_for_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder
write.csv(TBATS_Four_forecast, "Output/TBATS_Four_forecast.csv", row.names = FALSE)

```

### Model 4: Neural Network [2,3]
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 23 
NN_fit23_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,3)))

NN_for23_fulltrain <- forecast(NN_fit23_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,3),h=59))

# Plot foresting results
autoplot(NN_for23_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for23_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast23 <- as.data.frame(NN_for23_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast23, "Output/NN_forecast23.csv", row.names = FALSE)

```

### Model 5: Neural Network [2,2]
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 22
NN_fit22_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,2)))

NN_for22_fulltrain <- forecast(NN_fit22_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,2),h=59))

# Plot foresting results
autoplot(NN_for22_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for22_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast22 <- as.data.frame(NN_for22_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast22, "Output/NN_forecast22.csv", row.names = FALSE)
```

### Forecasting Temperature and Humidity 
```{r forecasting humidity}
# Create time series for only Feb 2010 
ts_Daily_Humidity <- ts_Daily_Electricity[,2]

# Use Models
ETS_fit_Hum <-  stlf(ts_Daily_Humidity, h = 59)

ARIMA_Four_fit_Hum <- auto.arima(ts_Daily_Humidity, seasonal=FALSE, lambda=0,
                                 xreg=fourier(ts_Daily_Humidity, K=c(2,3)))

ARIMA_Four_for_Hum <- forecast(ARIMA_Four_fit_Hum,
                               xreg=fourier(ts_Daily_Humidity,
                                            K=c(2,3), h=59), h=59)

TBATS_fit_Hum <- tbats(ts_Daily_Humidity)
TBATS_for_Hum <- forecast(TBATS_fit_Hum, h=59)

NN_fit23_Hum <- nnetar(ts_Daily_Humidity, p=1, P=0,
                             xreg=fourier(ts_Daily_Humidity, K=c(2,3)))

NN_for23_Hum <- forecast(NN_fit23_Hum, h=59, 
                               xreg=fourier(ts_Daily_Humidity, K=c(2,3),h=59))

# Accuracy Tests 
ETS_Hum <- accuracy(ETS_fit_Hum)  
ARIMA_Hum <- accuracy(ARIMA_Four_for_Hum)
TBATS_Hum <- accuracy(TBATS_for_Hum)
NN_Hum <- accuracy(NN_for23_Hum)

# Create data frame
scores_Hum <- as.data.frame(
  rbind(ETS_Hum, ARIMA_Hum, TBATS_Hum, NN_Hum))
row.names(scores_Hum) <- c("STL+ETS", "ARIMA+Fourier","TBATS","NN23")

# Choose model with lowest MAPE
best_model_index <- which.min(scores_Hum[,"MAPE"])
cat("The best model by MAPE is:", row.names(scores_Hum[best_model_index,])) # STL + ETS is the best model. 

# Forecast humidity for Jan and Feb 2011 
Hum_2011 <- as.data.frame(ETS_fit_Hum$mean) %>%
  rename(Forcast_Hum = 1) %>%  
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", length.out = 59)) %>%  
  select(date, Forcast_Hum)
```

```{r forecasting temperature}
# Create time series for only Feb 2010 
ts_Daily_Temp <- ts_Daily_Electricity[,3]

# Use Models
ETS_fit_Temp <-  stlf(ts_Daily_Temp, h = 59)

ARIMA_Four_fit_Temp <- auto.arima(ts_Daily_Temp, seasonal=FALSE, lambda=0,
                                 xreg=fourier(ts_Daily_Temp, K=c(2,3)))

ARIMA_Four_for_Temp <- forecast(ARIMA_Four_fit_Temp,
                               xreg=fourier(ts_Daily_Temp,
                                            K=c(2,3), h=59), h=59)

TBATS_fit_Temp <- tbats(ts_Daily_Temp)
TBATS_for_Temp <- forecast(TBATS_fit_Temp, h=59)

NN_fit23_Temp<- nnetar(ts_Daily_Temp, p=1, P=0,
                             xreg=fourier(ts_Daily_Temp, K=c(2,3)))

NN_for23_Temp <- forecast(NN_fit23_Hum, h=59, 
                               xreg=fourier(ts_Daily_Temp, K=c(2,3),h=59))

# Accuracy Tests 
ETS_Temp <- accuracy(ETS_fit_Temp)  
ARIMA_Temp <- accuracy(ARIMA_Four_for_Temp)
TBATS_Temp <- accuracy(TBATS_for_Temp)
NN_Temp <- accuracy(NN_for23_Temp)

# Create data frame
scores_Temp <- as.data.frame(
  rbind(ETS_Temp, ARIMA_Temp, TBATS_Temp, NN_Temp))
row.names(scores_Temp) <- c("STL+ETS", "ARIMA+Fourier","TBATS","NN23")

# Choose model with lowest MAPE
best_model_index <- which.min(scores_Temp[,"MAPE"])
cat("The best model by MAPE is:", row.names(scores_Hum[best_model_index,])) # STL + ETS is the best model. 

# Forecast humidity for Jan and Feb 2011 
Temp_2011 <- as.data.frame(ETS_fit_Temp$mean) %>%
  rename(Forcast_Temp = 1) %>%  
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", length.out = 59)) %>%  
  select(date, Forcast_Temp)
```

### Model 6: ARIMA + FOURIER terms + TempHum 
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_full <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3))
temp_full <- as.numeric(Daily_Electricity$Daily_temp)
humidity_full <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_combinedfull <- cbind(fourier_full, temp = temp_full, humidity = humidity_full)

# Generate Fourier + exogenous variables for forecasting
fourier_forfull <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3), h = 59)
temp_forfull <- as.numeric(Temp_2011$Forcast_Temp)
humidity_forfull <- as.numeric(Hum_2011$Forcast_Hum)
fourier_combined_forfull <- cbind(fourier_forfull, temp = temp_forfull, humidity = humidity_forfull)

# Match column names
colnames(fourier_combined_forfull) <- colnames(fourier_combinedfull)

# Fit and Forecast Model
ARIMA_Fourexo_fit_fulltrain <- auto.arima(ts_Daily_Electricity_fulltrain, 
                                 seasonal = FALSE, 
                                 lambda = 0,
                                 xreg = fourier_combinedfull)

ARIMA_Fourexo_for_fulltrain <- forecast(ARIMA_Fourexo_fit_fulltrain,
                               xreg = fourier_combined_forfull,
                               h = 59)

# Plot foresting results
autoplot(ARIMA_Fourexo_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Fourexo_for_fulltrain, series="ARIMA + Fourier + TempHum Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ARIMA_Fourexo_forecast <- as.data.frame(ARIMA_Fourexo_for_fulltrain$mean) %>%
  rename(load = 1) %>% 
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(ARIMA_Fourexo_forecast, "Output/ARIMA_Fourexo_forecast.csv", row.names = FALSE)
```

### Model 7: ARIMA + FOURIER terms + Temp
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_fullT <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3))
temp_fullT <- as.numeric(Daily_Electricity$Daily_temp)
fourier_combinedfullT <- cbind(fourier_fullT, temp = temp_fullT)

# Generate Fourier + exogenous variables for forecasting
fourier_forfullT <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3), h = 59)
temp_forfullT <- as.numeric(Temp_2011$Forcast_Temp)
fourier_combined_forfullT <- cbind(fourier_forfullT, temp = temp_forfullT)

# Match column names
colnames(fourier_combined_forfullT) <- colnames(fourier_combinedfullT)

# Fit and Forecast Model
ARIMA_Fourexo_fit_fulltrainT <- auto.arima(ts_Daily_Electricity_fulltrain, 
                                           seasonal = FALSE, 
                                           lambda = 0,
                                           xreg = fourier_combinedfullT)

ARIMA_Fourexo_for_fulltrainT <- forecast(ARIMA_Fourexo_fit_fulltrainT,
                                         xreg = fourier_combined_forfullT,
                                         h = 59)

# Plot foresting results
autoplot(ARIMA_Fourexo_for_fulltrainT) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Fourexo_for_fulltrainT, series="ARIMA + Fourier + Temp Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ARIMA_Fourexo_forecastT <- as.data.frame(ARIMA_Fourexo_for_fulltrainT$mean) %>%
  rename(load = 1) %>% 
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(ARIMA_Fourexo_forecastT, "Output/ARIMA_Fourexo_forecastT.csv", row.names = FALSE)
```

### Model 8: Neural Network [2,2] + Exo
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_nnfull <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 2))
temp_nnfull <- as.numeric(Daily_Electricity$Daily_temp)
humidity_nnfull <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_nncombinedfull <- cbind(fourier_nnfull, temp = temp_nnfull, humidity = humidity_nnfull)

# Generate Fourier + exogenous variables for forecasting
fourier_nnforfull <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 2), h = 59)
temp_nnforfull <- as.numeric(Temp_2011$Forcast_Temp)
humidity_nnforfull <- as.numeric(Hum_2011$Forcast_Hum)
fourier_combined_nnforfull <- cbind(fourier_nnforfull, temp = temp_nnforfull, humidity = humidity_nnforfull)
# Match column names between training and forecast xreg
colnames(fourier_combined_nnforfull) <- colnames(fourier_nncombinedfull)

# Fit and Forecast the model 
NNexo_fit22_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                      p = 1,
                      P = 0,
                      xreg = fourier_nncombinedfull)

NNexo_for22_fulltrain <- forecast(NNexo_fit22_fulltrain,
                        h = 59,
                        xreg = fourier_combined_nnforfull)

# Plot foresting results
autoplot(NNexo_for22_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NNexo_for22_fulltrain, series="Neural Network [22] + Exo Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NNexo_forecast22 <- as.data.frame(NNexo_for22_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NNexo_forecast22, "Output/NNexo_forecast22.csv", row.names = FALSE)
```

### Model 9: Neural Network [2,3] + Exo
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_nnfullT <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3))
temp_nnfullT <- as.numeric(Daily_Electricity$Daily_temp)
humidity_nnfullT <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_nncombinedfullT <- cbind(fourier_nnfullT, temp = temp_nnfullT, humidity = humidity_nnfullT)

# Generate Fourier + exogenous variables for forecasting
fourier_nnforfullT <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3), h = 59)
temp_nnforfullT <- as.numeric(Temp_2011$Forcast_Temp)
humidity_nnforfullT <- as.numeric(Hum_2011$Forcast_Hum)
fourier_combined_nnforfullT <- cbind(fourier_nnforfullT, temp = temp_nnforfullT, humidity = humidity_nnforfullT)
# Match column names between training and forecast xreg
colnames(fourier_combined_nnforfullT) <- colnames(fourier_nncombinedfullT)

# Fit and Forecast the model 
NNexo_fit23_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                      p = 1,
                      P = 0,
                      xreg = fourier_nncombinedfullT)

NNexo_for23_fulltrain <- forecast(NNexo_fit23_fulltrain,
                        h = 59,
                        xreg = fourier_combined_nnforfullT)

# Plot foresting results
autoplot(NNexo_for23_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NNexo_for23_fulltrain, series="Neural Network [23] + Exo Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NNexo_forecast23 <- as.data.frame(NNexo_for23_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NNexo_forecast23, "Output/NNexo_forecast23.csv", row.names = FALSE)
```

### Model 10: Neural Network [223]
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 22
NN_fit223_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=3,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,2)))

NN_for223_fulltrain <- forecast(NN_fit223_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,2),h=59))

# Plot foresting results
autoplot(NN_for223_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for223_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast223 <- as.data.frame(NN_for223_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast223, "Output/NN_forecast223.csv", row.names = FALSE)
```

### Model 11: Neural Network [223] + TBATS 
```{r}
stl <- as.numeric(ETS_fit_fulltrain$mean)
nn223 <- as.numeric(NN_for223_fulltrain$mean)

avg <- (stl + nn223) / 2

# Create date index for forecast
start_date <- as.Date(paste0(end(Daily_Electricity$Date)[1] + 1, "-", end(Daily_Electricity$Date)[2], "-01")) 
forecast_dates <- seq(from = as.Date("2011-01-01"), by = "day", length.out = n_for)

Combined <- tibble(
  date = forecast_dates,
  load = avg
)

ggplot(Combined, aes(x = date, y = load)) +
  geom_line(color = "blue") +
  labs(
    title = "Forecasted Load Over Time",
    x = "Date",
    y = "Average Load"
  ) +
  theme_minimal()

# Save forecast in the output folder 
write.csv(Combined, "Output/Combined.csv", row.names = FALSE)
```

