---
title: "Forecasting Competition_Part II"
author: "Alex Lopez and Aye Nyein Thu"
date: "2025-03-23"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages
```{r load packages, message=FALSE, warning=FALSE}
# Load required packages
library(readxl)
library(openxlsx)
library(writexl)
library(dplyr)
library(lubridate)
library(ggplot2)
library(cowplot)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(smooth)
library(kableExtra)
library(car)

# Check working directory
getwd()
```

## Importing data sets
```{r import demand data set, results='hide', warning=FALSE, message=FALSE}
## Raw Data: Electricity Demand 
# Import the data set
Demand <- read_excel(
  path = "./Data/Raw/load.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Demand <- Demand %>%
  pivot_longer(cols = starts_with("h"), 
               names_to = "hour", 
               values_to = "Hourly_demand") %>%
  mutate(Hour = as.numeric(sub("h", "", hour))) %>%
  mutate(Date = ymd(date)) %>% 
  select(Date, Hour, Hourly_demand)

summary(Hourly_Demand) # Note the 6 missing values
 
# Format the daily data set 
Daily_Demand  <- Hourly_Demand %>%
  filter( !is.na(Hourly_demand)) %>% 
  group_by(Date) %>% 
  summarise(Daily_demand = mean(Hourly_demand)) 

## Raw Data: Relative Humidity 
# Import the data set
Humidity <- read_excel(
  path = "./Data/Raw/relative_humidity.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Humidity <- Humidity %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_humidity = rowMeans(select(.,rh_ws1:rh_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_humidity)

# Format the daily data set 
Daily_Humidity  <- Hourly_Humidity %>%
  group_by(Date) %>% 
  summarise(Daily_humidity = mean(Hourly_humidity)) 

## Raw Data: Temperature 
# Import the data set
Temperature <- read_excel(
  path = "./Data/Raw/temperature.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Temperature <- Temperature %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_temp = rowMeans(select(.,t_ws1:t_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_temp)

# Format the daily data set 
Daily_Temperature  <- Hourly_Temperature %>%
  group_by(Date) %>% 
  summarise(Daily_temp = mean(Hourly_temp)) 
```

## Data Wrangling 
```{r combining data set, results='hide', warning=FALSE, message=FALSE}
# Combine the hourly data set
Hourly_Electricity <- Hourly_Demand %>% 
  left_join(Hourly_Humidity, by = c("Date", "Hour")) %>% 
  left_join(Hourly_Temperature, by = c("Date", "Hour"))

summary(Hourly_Electricity) # Note the 6 missing values
  
# Combine the daily data set using the simple average 
Daily_Electricity <- Daily_Demand %>% 
  left_join(Daily_Humidity, by = "Date")  %>% 
  left_join(Daily_Temperature, by = "Date")
  
# Save the processed data sets in the folder 
#write.xlsx(Hourly_Electricity, "Data/Processed/Hourly_Electricity.xlsx") 
#write.xlsx(Daily_Electricity, "Data/Processed/Daily_Electricity.xlsx")
```

## Initial Data Exploration 
```{r initial plots, message=FALSE, warning=FALSE}}
# Hourly 
ggplot(Hourly_Electricity, aes(x=Date)) +
  geom_line(aes(y=Hourly_demand), color="blue") 

# Daily using simple average 
ggplot(Daily_Electricity, aes(x=Date)) +
  geom_line(aes(y=Daily_demand), color="blue") 
```

## Transforming into Time Series 
```{r tranform into time series, warning=FALSE, message=FALSE}
# Transform data into time series 
ts_Hourly_Electricity <- msts(Hourly_Electricity[,3:5], 
                             seasonal.periods = c(24,168,8766),
                             start = c(2005, 1, 1, 1)) # Added the hour

ts_Daily_Electricity <- msts(Daily_Electricity[,2:4], 
                             seasonal.periods = c(7, 365.25),
                             start = c(2005, 1, 1))
```

## Handling missing values and outliers
```{r missing values and outliers, warning=FALSE, message=FALSE}
# Check missing values 
sum(is.na(ts_Hourly_Electricity))
sum(is.na(ts_Daily_Electricity))

# Check outlier by test
outlier(ts_Hourly_Electricity) 
grubbs.test(ts_Hourly_Electricity[,1]) # It is outlier. 
grubbs.test(ts_Hourly_Electricity[,2]) # It is not outlier. 
grubbs.test(ts_Hourly_Electricity[,3]) # It is not outlier. 

outlier(ts_Daily_Electricity)
grubbs.test(ts_Daily_Electricity[,1]) # It is not outlier. 
grubbs.test(ts_Daily_Electricity[,2]) # It is not outlier. 
grubbs.test(ts_Daily_Electricity[,3]) # It is not outlier. 

# Handle missing values and outliers for the hourly data 
Cleaned_HDemand <- tsclean(ts_Hourly_Electricity[,1]) 
outlier(Cleaned_HDemand) 
grubbs.test(Cleaned_HDemand) # It is not outlier. 

autoplot(ts_Hourly_Electricity[,1], series="Raw Data") +
  autolayer(Cleaned_HDemand, series="Cleaned Data") +
  ylab("Hourly Electricity") # Only two data points are corrected. 
```

## Daily Demand 
### Decomposition and Setting training and testing windows
```{r daily data set decompose, message=FALSE, warning=FALSE}
# Daily Data Set
# Decompose the time series
ts_Daily_Electricity_decompose <- mstl(ts_Daily_Electricity[,1])
autoplot(ts_Daily_Electricity_decompose)
```

```{r daily data set training and testing, message=FALSE, warning=FALSE}
n_for = 59

# Create time series for only Feb 2010 
ts_Daily_Electricity_Feb <- subset(ts_Daily_Electricity[,1],
                                   end = length(ts_Daily_Electricity[,1])-(365-n_for))

# Create a subset for training purpose
ts_Daily_Electricity_train <- subset(ts_Daily_Electricity_Feb,
                                   end = length(ts_Daily_Electricity_Feb)-n_for)

# Create a subset for testing purpose
ts_Daily_Electricity_test <- subset(ts_Daily_Electricity_Feb,
                                   start = length(ts_Daily_Electricity_Feb)-n_for+1)

autoplot(ts_Daily_Electricity_train)
autoplot(ts_Daily_Electricity_test)

# Print the first and last 5 rows to check 
head(ts_Daily_Electricity_train, 5)
tail(ts_Daily_Electricity_train, 5)

head(ts_Daily_Electricity_test, 5)
tail(ts_Daily_Electricity_test, 5)
```

### Generating Time Series Model for Daiy Data Set
#### Model 1: STL + ETS
```{r Daily Model 1: STL + ETS, message=FALSE, warning=FALSE}
# Fit and forecast STL + ETS model to data
ETS_fit <-  stlf(ts_Daily_Electricity_train, h = 59)

# Plot foresting results
autoplot(ETS_fit) + ylab("Daily Electricity Demand")

# Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(ETS_fit, series="STL + ETS",PI=FALSE) +
  ylab("Daily Electricity Demand")
```

#### Model 2: ARIMA + FOURIER terms
```{r Daily Model 2: ARIMA + FOURIER, message=FALSE, warning=FALSE}
# Fit arima model with fourier terms as exogenous regressors
ARIMA_Four_fit <- auto.arima(ts_Daily_Electricity_train, 
                             seasonal=FALSE, 
                             lambda=0,
                             xreg=fourier(ts_Daily_Electricity_train,
                                          K=c(2,3)) 
                             )

ARIMA_Four_for <- forecast(ARIMA_Four_fit,
                           xreg=fourier(ts_Daily_Electricity_train,
                                        K=c(2,3),
                                        h=59),
                           h=59
                           ) 

#Plot foresting results
autoplot(ARIMA_Four_for) + ylab("Total Electricity Demand")

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(ARIMA_Four_for, series="ARIMA_FOURIER",PI=FALSE) +
  ylab("Total Electricity Demand")
```

#### Model 3: TBATS
```{r Daily Model 3: TBATS, message=FALSE, warning=FALSE}
# Fit TBATS Model
TBATS_fit <- tbats(ts_Daily_Electricity_train)

TBATS_for <- forecast(TBATS_fit, h=59)

#Plot foresting results
autoplot(TBATS_for) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(TBATS_for, series="TBATS",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

#### Model 4: Neural Network Time Series Forecasts [2,3]
```{r Daily Model 4: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit23 <- nnetar(ts_Daily_Electricity_train,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,3)))

NN_for23 <- forecast(NN_fit23, h=59,xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,3),h=59))


#Plot foresting results
autoplot(NN_for23) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for23, series="Neural Network 23",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

#### Model 5: Neural Network Time Series Forecasts [2,2]
```{r Daily Model 5: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit22 <- nnetar(ts_Daily_Electricity_train,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,2)))

NN_for22 <- forecast(NN_fit22, h=59,xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,2),h=59))


#Plot foresting results
autoplot(NN_for22) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NN_for22, series="Neural Network 22",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

#### Exogenous Variables 
```{r VIF test}
# Correlation Test 
cor.test(Daily_Electricity$Daily_demand, Daily_Electricity$Daily_temp) # Weak negative correlation
cor.test(Daily_Electricity$Daily_demand, Daily_Electricity$Daily_humidity) # Weak negative correlation 
cor.test(Daily_Electricity$Daily_temp, Daily_Electricity$Daily_humidity) # Moderate positive correlation 

# VIF Test
LM_model <- lm(Daily_demand ~ Daily_temp + Daily_humidity, data = Daily_Electricity)
summary(LM_model)

vif(LM_model) # Test scores less than the standard threshold 5 (Hence, Low Multi-collinearity) 
```

#### Model 6: ARIMA + FOURIER terms + TempHum 
```{r Daily Model 6: ARIMA + FOURIER + Exo, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier <- fourier(ts_Daily_Electricity_train, K = c(2, 3))
temp <- as.numeric(Daily_Electricity$Daily_temp[1:1826])
humidity <- as.numeric(Daily_Electricity$Daily_humidity[1:1826])
fourier_combined <- cbind(fourier, temp = temp, humidity = humidity)

# Generate Fourier + exogenous variables for forecasting
fourier_for <- fourier(ts_Daily_Electricity_train, K = c(2, 3), h = 59)
temp_for <- as.numeric(Daily_Electricity$Daily_temp[1827:1885])
humidity_for <- as.numeric(Daily_Electricity$Daily_humidity[1827:1885])
fourier_combined_for <- cbind(fourier_for, temp = temp_for, humidity = humidity_for)

# Match column names
colnames(fourier_combined_for) <- colnames(fourier_combined)

# Fit and Forecast Model
ARIMA_Fourexo_fit <- auto.arima(ts_Daily_Electricity_train, 
                                 seasonal = FALSE, 
                                 lambda = 0,
                                 xreg = fourier_combined)

ARIMA_Fourexo_for <- forecast(ARIMA_Fourexo_fit,
                               xreg = fourier_combined_for,
                               h = 59)

#Plot foresting results
autoplot(ARIMA_Fourexo_for) + ylab("Total Electricity Demand")

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(ARIMA_Fourexo_for, series="ARIMA_FOURIER + TempHum",PI=FALSE) +
  ylab("Total Electricity Demand")
```

#### Model 7: ARIMA + FOURIER terms + Temp
```{r Daily Model 7: ARIMA + FOURIER + Temp, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourierT <- fourier(ts_Daily_Electricity_train, K = c(2, 3))
tempT <- as.numeric(Daily_Electricity$Daily_temp[1:1826])
fourier_combinedT <- cbind(fourier, temp = tempT)

# Generate Fourier + exogenous variables for forecasting
fourier_forT <- fourier(ts_Daily_Electricity_train, K = c(2, 3), h = 59)
temp_forT <- as.numeric(Daily_Electricity$Daily_temp[1827:1885])
fourier_combined_forT <- cbind(fourier_forT, temp = temp_forT)

# Match column names
colnames(fourier_combined_forT) <- colnames(fourier_combinedT)

# Fit and Forecast Model
ARIMA_Fourexo_fitT <- auto.arima(ts_Daily_Electricity_train, 
                                 seasonal = FALSE, 
                                 lambda = 0,
                                 xreg = fourier_combinedT)

ARIMA_Fourexo_forT <- forecast(ARIMA_Fourexo_fitT,
                               xreg = fourier_combined_forT,
                               h = 59)

#Plot foresting results
autoplot(ARIMA_Fourexo_forT) + ylab("Total Electricity Demand")

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(ARIMA_Fourexo_forT, series="ARIMA_FOURIER + Temp",PI=FALSE) +
  ylab("Total Electricity Demand")
```

#### Model 8: Neural Network Time Series Forecasts [2,2] + Exo 
```{r Daily Model 8: NN22 + Exo, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_nn <- fourier(ts_Daily_Electricity_train, K = c(2, 2))
temp_nn <- as.numeric(Daily_Electricity$Daily_temp[1:1826])
humidity_nn <- as.numeric(Daily_Electricity$Daily_humidity[1:1826])
fourier_nncombined <- cbind(fourier_nn, temp = temp_nn, humidity = humidity_nn)

# Generate Fourier + exogenous variables for forecasting
fourier_nnfor <- fourier(ts_Daily_Electricity_train, K = c(2, 2), h = 59)
temp_nnfor <- as.numeric(Daily_Electricity$Daily_temp[1827:1885])
humidity_nnfor <- as.numeric(Daily_Electricity$Daily_humidity[1827:1885])
fourier_combined_nnfor <- cbind(fourier_nnfor, temp = temp_nnfor, humidity = humidity_nnfor)

# Match column names between training and forecast xreg
colnames(fourier_combined_nnfor) <- colnames(fourier_nncombined)

# Fit and Forecast the model 
NNexo_fit22 <- nnetar(ts_Daily_Electricity_train,
                      p = 1,
                      P = 0,
                      xreg = fourier_nncombined)

NNexo_for22 <- forecast(NNexo_fit22,
                        h = 59,
                        xreg = fourier_combined_nnfor)

#Plot foresting results
autoplot(NNexo_for22) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NNexo_for22, series="Neural Network 22 + Exo",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

#### Model 9: Neural Network Time Series Forecasts [2,3] + Exo 
```{r Daily Model 9: NN23 + Exo, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_nnT <- fourier(ts_Daily_Electricity_train, K = c(2, 3))
temp_nnT <- as.numeric(Daily_Electricity$Daily_temp[1:1826])
humidity_nnT <- as.numeric(Daily_Electricity$Daily_humidity[1:1826])
fourier_nncombinedT <- cbind(fourier_nnT, temp = temp_nnT, humidity = humidity_nnT)

# Generate Fourier + exogenous variables for forecasting
fourier_nnforT <- fourier(ts_Daily_Electricity_train, K = c(2, 3), h = 59)
temp_nnforT <- as.numeric(Daily_Electricity$Daily_temp[1827:1885])
humidity_nnforT <- as.numeric(Daily_Electricity$Daily_humidity[1827:1885])
fourier_combined_nnforT <- cbind(fourier_nnforT, temp = temp_nnforT, humidity = humidity_nnforT)

# Match column names between training and forecast xreg
colnames(fourier_combined_nnforT) <- colnames(fourier_nncombinedT)

# Fit and Forecast the model 
NNexo_fit23 <- nnetar(ts_Daily_Electricity_train,
                      p = 1,
                      P = 0,
                      xreg = fourier_nncombinedT)

NNexo_for23 <- forecast(NNexo_fit23,
                        h = 59,
                        xreg = fourier_combined_nnforT)

#Plot foresting results
autoplot(NNexo_for23) +
  ylab("Total Electricity Demand") 

#Plot model + observed data
autoplot(ts_Daily_Electricity_Feb) +
  autolayer(NNexo_for23, series="Neural Network 23 + Exo",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

## Accuracy and Performance Testing
```{r daily model accuracy and performance, warning=FALSE, message=FALSE}
# Model 1: STL + ETS
ETS_scores <- accuracy(ETS_fit$mean,ts_Daily_Electricity_test)  

# Model 2: ARIMA + Fourier 
ARIMA_scores <- accuracy(ARIMA_Four_for$mean,ts_Daily_Electricity_test)

# Model 3:  TBATS 
TBATS_scores <- accuracy(TBATS_for$mean,ts_Daily_Electricity_test)

# Model 4:  Neural Network 23
NN_scores23 <- accuracy(NN_for23$mean,ts_Daily_Electricity_test)

# Model 5:  Neural Network 22
NN_scores22 <- accuracy(NN_for22$mean,ts_Daily_Electricity_test)

# Model 6: ARIMA + Fourier + TempHum
ARIMAexo_scoresTH <- accuracy(ARIMA_Fourexo_for$mean,ts_Daily_Electricity_test)

# Model 7: ARIMA + Fourier + Temp
ARIMAexo_scoresT <- accuracy(ARIMA_Fourexo_forT$mean,ts_Daily_Electricity_test)

# Model 8:  Neural Network 22 + Exo
NNexo_scores22 <- accuracy(NNexo_for22$mean,ts_Daily_Electricity_test)

# Model 9:  Neural Network 23 + Exo
NNexo_scores23 <- accuracy(NNexo_for23$mean,ts_Daily_Electricity_test)

# Create data frame
scores <- as.data.frame(
  rbind(ETS_scores, ARIMA_scores, TBATS_scores, NN_scores23, NN_scores22, ARIMAexo_scoresTH, ARIMAexo_scoresT, NNexo_scores22, NNexo_scores23)
  )
row.names(scores) <- c("STL+ETS", "ARIMA+Fourier","TBATS","NN23", "NN22", "ARIMA+Fourier+TH","ARIMA+Fourier+T", "NN22+Exo", "NN23+Exo")

# Choose model with lowest MAPE
best_model_index <- which.min(scores[,"MAPE"])
cat("The best model by MAPE is:", row.names(scores[best_model_index,])) 

# Construct tables
kbl(scores, 
      caption = "Forecast Accuracy for Daily Total Electricity Demand",
      digits = array(5,ncol(scores))) %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = "hold_position") %>%
  kable_styling(latex_options="striped", stripe_index = which.min(scores[,"MAPE"]))

# Plot 
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ETS_fit, PI=FALSE, series="STL+ETS") +
  autolayer(ARIMA_Four_for, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(TBATS_for,PI=FALSE, series="TBATS") +
  autolayer(NN_for23,PI=FALSE, series="NN23") +
  autolayer(NN_for22,PI=FALSE, series="NN22") +
  autolayer(ARIMA_Fourexo_for, PI=FALSE, series="ARIMA + Fourier + TempHum") +
  autolayer(ARIMA_Fourexo_forT, PI=FALSE, series="ARIMA + Fourier + Temp") + 
  autolayer(NNexo_for22,PI=FALSE, series="NN22 + Exo") + 
  autolayer(NNexo_for23,PI=FALSE, series="NN23 + Exo") + 
  xlab("Day") + ylab("Daily Electricity Deamand") +
  guides(colour=guide_legend(title="Forecast"))

autoplot(ts_Daily_Electricity_test) +
  autolayer(ETS_fit, PI=FALSE, series="STL+ETS") +
  autolayer(ARIMA_Four_for, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(TBATS_for,PI=FALSE, series="TBATS") +
  autolayer(NN_for23,PI=FALSE, series="NN") +
  autolayer(NN_for22,PI=FALSE, series="NN22") +
  autolayer(ARIMA_Fourexo_for, PI=FALSE, series="ARIMA + Fourier + TempHum") +
  autolayer(ARIMA_Fourexo_forT, PI=FALSE, series="ARIMA + Fourier + Temp") +
  autolayer(NNexo_for22,PI=FALSE, series="NN22 + Exo") +
  autolayer(NNexo_for23,PI=FALSE, series="NN23 + Exo") +
  ylab("Daily Electricity Deamand") +
  guides(colour=guide_legend(title="Forecast"))
```

## Forecasting for 2011 with fulltrain data set
```{r create full train time series, message=FALSE, warning=}
# Create the time series to retain full data set
ts_Daily_Electricity_fulltrain <- ts_Daily_Electricity[,1]
```

### Model 1: STL + ETS
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained STL+ETS Model 
ETS_fit_fulltrain <- stlf(ts_Daily_Electricity_fulltrain, h = 59)

# Plot foresting results
autoplot(ETS_fit_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ETS_fit_fulltrain, series="STL + ETS Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ETS_forecast <- as.data.frame(ETS_fit_fulltrain$mean) %>%
  rename(load = 1) %>%  
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%  
  select(date, load)

# Save forecast in the output folder 
write.csv(ETS_forecast, "Output/ETS_forecast.csv", row.names = FALSE)
```

### Model 2: ARIMA + FOURIER terms
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained ARIMA + Fourier terms Model 
ARIMA_Four_fit_fulltrain <- auto.arima(ts_Daily_Electricity_fulltrain, 
                                       seasonal=FALSE, 
                                       lambda=0,
                                       xreg=fourier(ts_Daily_Electricity_fulltrain,
                                                    K=c(2,3)) 
                                       )

ARIMA_Four_for_fulltrain <- forecast(ARIMA_Four_fit_fulltrain,
                                     xreg=fourier(ts_Daily_Electricity_fulltrain,
                                                  K=c(2,3),
                                                  h=59),
                                     h=59
                                     )

# Plot foresting results
autoplot(ARIMA_Four_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Four_for_fulltrain, series="ARIMA + Fourier Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ARIMA_Four_forecast <- as.data.frame(ARIMA_Four_for_fulltrain$mean) %>%
  rename(load = 1) %>% 
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(ARIMA_Four_forecast, "Output/ARIMA_Four_forecast.csv", row.names = FALSE)
```

### Model 3: TBATS
``` {r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained TBATS Model 
TBATS_fit_fulltrain <- tbats(ts_Daily_Electricity_fulltrain)

TBATS_for_fulltrain <- forecast(TBATS_fit_fulltrain, h=59)
  
# Plot foresting results
autoplot(TBATS_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(TBATS_for_fulltrain, series="TBATS Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
TBATS_Four_forecast <- as.data.frame(TBATS_for_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder
write.csv(TBATS_Four_forecast, "Output/TBATS_Four_forecast.csv", row.names = FALSE)

```

### Model 4: Neural Network [2,3]
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 23 
NN_fit23_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,3)))

NN_for23_fulltrain <- forecast(NN_fit23_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,3),h=59))

# Plot foresting results
autoplot(NN_for23_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for23_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast23 <- as.data.frame(NN_for23_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast23, "Output/NN_forecast23.csv", row.names = FALSE)

```

### Model 5: Neural Network [2,2]
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 22
NN_fit22_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,2)))

NN_for22_fulltrain <- forecast(NN_fit22_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,2),h=59))

# Plot foresting results
autoplot(NN_for22_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for22_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast22 <- as.data.frame(NN_for22_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast22, "Output/NN_forecast22.csv", row.names = FALSE)
```

### Forecasting Temperature and Humidity 
```{r forecasting humidity}
# Create time series for only Feb 2010 
ts_Daily_Humidity <- ts_Daily_Electricity[,2]

# Use Models
ETS_fit_Hum <-  stlf(ts_Daily_Humidity, h = 59)

ARIMA_Four_fit_Hum <- auto.arima(ts_Daily_Humidity, seasonal=FALSE, lambda=0,
                                 xreg=fourier(ts_Daily_Humidity, K=c(2,3)))

ARIMA_Four_for_Hum <- forecast(ARIMA_Four_fit_Hum,
                               xreg=fourier(ts_Daily_Humidity,
                                            K=c(2,3), h=59), h=59)

TBATS_fit_Hum <- tbats(ts_Daily_Humidity)
TBATS_for_Hum <- forecast(TBATS_fit_Hum, h=59)

NN_fit23_Hum <- nnetar(ts_Daily_Humidity, p=1, P=0,
                             xreg=fourier(ts_Daily_Humidity, K=c(2,3)))

NN_for23_Hum <- forecast(NN_fit23_Hum, h=59, 
                               xreg=fourier(ts_Daily_Humidity, K=c(2,3),h=59))

# Accuracy Tests 
ETS_Hum <- accuracy(ETS_fit_Hum)  
ARIMA_Hum <- accuracy(ARIMA_Four_for_Hum)
TBATS_Hum <- accuracy(TBATS_for_Hum)
NN_Hum <- accuracy(NN_for23_Hum)

# Create data frame
scores_Hum <- as.data.frame(
  rbind(ETS_Hum, ARIMA_Hum, TBATS_Hum, NN_Hum))
row.names(scores_Hum) <- c("STL+ETS", "ARIMA+Fourier","TBATS","NN23")

# Choose model with lowest MAPE
best_model_index <- which.min(scores_Hum[,"MAPE"])
cat("The best model by MAPE is:", row.names(scores_Hum[best_model_index,])) # STL + ETS is the best model. 

# Forecast humidity for Jan and Feb 2011 
Hum_2011 <- as.data.frame(ETS_fit_Hum$mean) %>%
  rename(Forcast_Hum = 1) %>%  
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", length.out = 59)) %>%  
  select(date, Forcast_Hum)
```

```{r forecasting temperature}
# Create time series for only Feb 2010 
ts_Daily_Temp <- ts_Daily_Electricity[,3]

# Use Models
ETS_fit_Temp <-  stlf(ts_Daily_Temp, h = 59)

ARIMA_Four_fit_Temp <- auto.arima(ts_Daily_Temp, seasonal=FALSE, lambda=0,
                                 xreg=fourier(ts_Daily_Temp, K=c(2,3)))

ARIMA_Four_for_Temp <- forecast(ARIMA_Four_fit_Temp,
                               xreg=fourier(ts_Daily_Temp,
                                            K=c(2,3), h=59), h=59)

TBATS_fit_Temp <- tbats(ts_Daily_Temp)
TBATS_for_Temp <- forecast(TBATS_fit_Temp, h=59)

NN_fit23_Temp<- nnetar(ts_Daily_Temp, p=1, P=0,
                             xreg=fourier(ts_Daily_Temp, K=c(2,3)))

NN_for23_Temp <- forecast(NN_fit23_Hum, h=59, 
                               xreg=fourier(ts_Daily_Temp, K=c(2,3),h=59))

# Accuracy Tests 
ETS_Temp <- accuracy(ETS_fit_Temp)  
ARIMA_Temp <- accuracy(ARIMA_Four_for_Temp)
TBATS_Temp <- accuracy(TBATS_for_Temp)
NN_Temp <- accuracy(NN_for23_Temp)

# Create data frame
scores_Temp <- as.data.frame(
  rbind(ETS_Temp, ARIMA_Temp, TBATS_Temp, NN_Temp))
row.names(scores_Temp) <- c("STL+ETS", "ARIMA+Fourier","TBATS","NN23")

# Choose model with lowest MAPE
best_model_index <- which.min(scores_Temp[,"MAPE"])
cat("The best model by MAPE is:", row.names(scores_Hum[best_model_index,])) # STL + ETS is the best model. 

# Forecast humidity for Jan and Feb 2011 
Temp_2011 <- as.data.frame(ETS_fit_Temp$mean) %>%
  rename(Forcast_Temp = 1) %>%  
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", length.out = 59)) %>%  
  select(date, Forcast_Temp)
```

### Model 6: ARIMA + FOURIER terms + TempHum 
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_full <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3))
temp_full <- as.numeric(Daily_Electricity$Daily_temp)
humidity_full <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_combinedfull <- cbind(fourier_full, temp = temp_full, humidity = humidity_full)

# Generate Fourier + exogenous variables for forecasting
fourier_forfull <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3), h = 59)
temp_forfull <- as.numeric(Temp_2011$Forcast_Temp)
humidity_forfull <- as.numeric(Hum_2011$Forcast_Hum)
fourier_combined_forfull <- cbind(fourier_forfull, temp = temp_forfull, humidity = humidity_forfull)

# Match column names
colnames(fourier_combined_forfull) <- colnames(fourier_combinedfull)

# Fit and Forecast Model
ARIMA_Fourexo_fit_fulltrain <- auto.arima(ts_Daily_Electricity_fulltrain, 
                                 seasonal = FALSE, 
                                 lambda = 0,
                                 xreg = fourier_combinedfull)

ARIMA_Fourexo_for_fulltrain <- forecast(ARIMA_Fourexo_fit_fulltrain,
                               xreg = fourier_combined_forfull,
                               h = 59)

# Plot foresting results
autoplot(ARIMA_Fourexo_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Fourexo_for_fulltrain, series="ARIMA + Fourier + TempHum Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ARIMA_Fourexo_forecast <- as.data.frame(ARIMA_Fourexo_for_fulltrain$mean) %>%
  rename(load = 1) %>% 
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(ARIMA_Fourexo_forecast, "Output/ARIMA_Fourexo_forecast.csv", row.names = FALSE)
```

### Model 7: ARIMA + FOURIER terms + Temp
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_fullT <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3))
temp_fullT <- as.numeric(Daily_Electricity$Daily_temp)
fourier_combinedfullT <- cbind(fourier_fullT, temp = temp_fullT)

# Generate Fourier + exogenous variables for forecasting
fourier_forfullT <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3), h = 59)
temp_forfullT <- as.numeric(Temp_2011$Forcast_Temp)
fourier_combined_forfullT <- cbind(fourier_forfullT, temp = temp_forfullT)

# Match column names
colnames(fourier_combined_forfullT) <- colnames(fourier_combinedfullT)

# Fit and Forecast Model
ARIMA_Fourexo_fit_fulltrainT <- auto.arima(ts_Daily_Electricity_fulltrain, 
                                           seasonal = FALSE, 
                                           lambda = 0,
                                           xreg = fourier_combinedfullT)

ARIMA_Fourexo_for_fulltrainT <- forecast(ARIMA_Fourexo_fit_fulltrainT,
                                         xreg = fourier_combined_forfullT,
                                         h = 59)

# Plot foresting results
autoplot(ARIMA_Fourexo_for_fulltrainT) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Fourexo_for_fulltrainT, series="ARIMA + Fourier + Temp Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ARIMA_Fourexo_forecastT <- as.data.frame(ARIMA_Fourexo_for_fulltrainT$mean) %>%
  rename(load = 1) %>% 
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(ARIMA_Fourexo_forecastT, "Output/ARIMA_Fourexo_forecastT.csv", row.names = FALSE)
```

### Model 8: Neural Network [2,2] + Exo
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_nnfull <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 2))
temp_nnfull <- as.numeric(Daily_Electricity$Daily_temp)
humidity_nnfull <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_nncombinedfull <- cbind(fourier_nnfull, temp = temp_nnfull, humidity = humidity_nnfull)

# Generate Fourier + exogenous variables for forecasting
fourier_nnforfull <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 2), h = 59)
temp_nnforfull <- as.numeric(Temp_2011$Forcast_Temp)
humidity_nnforfull <- as.numeric(Hum_2011$Forcast_Hum)
fourier_combined_nnforfull <- cbind(fourier_nnforfull, temp = temp_nnforfull, humidity = humidity_nnforfull)
# Match column names between training and forecast xreg
colnames(fourier_combined_nnforfull) <- colnames(fourier_nncombinedfull)

# Fit and Forecast the model 
NNexo_fit22_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                      p = 1,
                      P = 0,
                      xreg = fourier_nncombinedfull)

NNexo_for22_fulltrain <- forecast(NNexo_fit22_fulltrain,
                        h = 59,
                        xreg = fourier_combined_nnforfull)

# Plot foresting results
autoplot(NNexo_for22_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NNexo_for22_fulltrain, series="Neural Network [22] + Exo Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NNexo_forecast22 <- as.data.frame(NNexo_for22_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NNexo_forecast22, "Output/NNexo_forecast22.csv", row.names = FALSE)
```

### Model 9: Neural Network [2,3] + Exo
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_nnfullT <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3))
temp_nnfullT <- as.numeric(Daily_Electricity$Daily_temp)
humidity_nnfullT <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_nncombinedfullT <- cbind(fourier_nnfullT, temp = temp_nnfullT, humidity = humidity_nnfullT)

# Generate Fourier + exogenous variables for forecasting
fourier_nnforfullT <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3), h = 59)
temp_nnforfullT <- as.numeric(Temp_2011$Forcast_Temp)
humidity_nnforfullT <- as.numeric(Hum_2011$Forcast_Hum)
fourier_combined_nnforfullT <- cbind(fourier_nnforfullT, temp = temp_nnforfullT, humidity = humidity_nnforfullT)
# Match column names between training and forecast xreg
colnames(fourier_combined_nnforfullT) <- colnames(fourier_nncombinedfullT)

# Fit and Forecast the model 
NNexo_fit23_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                      p = 1,
                      P = 0,
                      xreg = fourier_nncombinedfullT)

NNexo_for23_fulltrain <- forecast(NNexo_fit23_fulltrain,
                        h = 59,
                        xreg = fourier_combined_nnforfullT)

# Plot foresting results
autoplot(NNexo_for23_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NNexo_for23_fulltrain, series="Neural Network [23] + Exo Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NNexo_forecast23 <- as.data.frame(NNexo_for23_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NNexo_forecast23, "Output/NNexo_forecast23.csv", row.names = FALSE)
```

```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 22
NN_fit223_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=3,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,2)))

NN_for223_fulltrain <- forecast(NN_fit223_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,2),h=59))

# Plot foresting results
autoplot(NN_for223_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for223_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast223 <- as.data.frame(NN_for223_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast223, "Output/NN_forecast223.csv", row.names = FALSE)
```