---
title: "Forecasting Competition_Part II"
author: "Alex Lopez and Aye Nyein Thu"
date: "2025-03-23"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages (Remove when combine)
```{r load packages, message=FALSE, warning=FALSE}
# Load required packages
library(readxl)
library(openxlsx)
library(writexl)
library(dplyr)
library(lubridate)
library(ggplot2)
library(cowplot)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(smooth)
library(kableExtra)
library(car)

# Check working directory
getwd()
```

## Importing data sets (Remove when combine)
```{r import demand data set, results='hide', warning=FALSE, message=FALSE}
## Raw Data: Electricity Demand 
# Import the data set
Demand <- read_excel(
  path = "./Data/Raw/load.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Demand <- Demand %>%
  pivot_longer(cols = starts_with("h"), 
               names_to = "hour", 
               values_to = "Hourly_demand") %>%
  mutate(Hour = as.numeric(sub("h", "", hour))) %>%
  mutate(Date = ymd(date)) %>% 
  select(Date, Hour, Hourly_demand)

summary(Hourly_Demand) # Note the 6 missing values
 
# Format the daily data set 
#Daily_Demand  <- Hourly_Demand %>%
  filter( !is.na(Hourly_demand)) %>% 
  group_by(Date) %>% 
  summarise(Daily_demand = mean(Hourly_demand)) 

## Raw Data: Relative Humidity 
# Import the data set
Humidity <- read_excel(
  path = "./Data/Raw/relative_humidity.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Humidity <- Humidity %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_humidity = rowMeans(select(.,rh_ws1:rh_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_humidity)

# Format the daily data set 
#Daily_Humidity  <- Hourly_Humidity %>%
  group_by(Date) %>% 
  summarise(Daily_humidity = mean(Hourly_humidity)) 

## Raw Data: Temperature 
# Import the data set
Temperature <- read_excel(
  path = "./Data/Raw/temperature.xlsx", sheet = "Sheet1", col_names = TRUE
)

# Format the hourly data set
Hourly_Temperature <- Temperature %>%
  mutate(Date = ymd(date), 
         Hour = hr, 
         Hourly_temp = rowMeans(select(.,t_ws1:t_ws28), na.rm = TRUE)) %>% 
  select(Date, Hour, Hourly_temp)

# Format the daily data set 
#Daily_Temperature  <- Hourly_Temperature %>%
  group_by(Date) %>% 
  summarise(Daily_temp = mean(Hourly_temp)) 
```

## Data Wrangling (Remove when combine)
```{r combining data set, results='hide', warning=FALSE, message=FALSE}
# Combine the hourly data set
Hourly_Electricity <- Hourly_Demand %>% 
  left_join(Hourly_Humidity, by = c("Date", "Hour")) %>% 
  left_join(Hourly_Temperature, by = c("Date", "Hour"))

summary(Hourly_Electricity) # Note the 6 missing values
  
# Combine the daily data set using the simple average 
#Daily_Electricity <- Daily_Demand %>% 
  left_join(Daily_Humidity, by = "Date")  %>% 
  left_join(Daily_Temperature, by = "Date")
  
# Save the processed data sets in the folder 
#write.xlsx(Hourly_Electricity, "Data/Processed/Hourly_Electricity.xlsx") 
#write.xlsx(Daily_Electricity, "Data/Processed/Daily_Electricity.xlsx")
```

## Transforming into Time Series (Remove when combine)
```{r tranform into time series, warning=FALSE, message=FALSE}
# Transform data into time series 
ts_Hourly_Electricity <- msts(Hourly_Electricity[,3:5], 
                             seasonal.periods = c(24,168,8766),
                             start = c(2005, 1, 1, 1)) # Added the hour

#ts_Daily_Electricity <- msts(Daily_Electricity[,2:4], 
                             seasonal.periods = c(7, 365.25),
                             start = c(2005, 1, 1))
```

## Handling missing values and outliers (Remove when combine)
```{r missing values and outliers, warning=FALSE, message=FALSE}
# Check missing values 
sum(is.na(ts_Hourly_Electricity))
sum(is.na(ts_Daily_Electricity))

# Check outlier by test
outlier(ts_Hourly_Electricity) 
grubbs.test(ts_Hourly_Electricity[,1]) # It is outlier. 
grubbs.test(ts_Hourly_Electricity[,2]) # It is not outlier. 
grubbs.test(ts_Hourly_Electricity[,3]) # It is not outlier. 

outlier(ts_Daily_Electricity)
grubbs.test(ts_Daily_Electricity[,1]) # It is not outlier. 
grubbs.test(ts_Daily_Electricity[,2]) # It is not outlier. 
grubbs.test(ts_Daily_Electricity[,3]) # It is not outlier. 

# Handle missing values and outliers for the hourly data 
Cleaned_HDemand <- tsclean(ts_Hourly_Electricity[,1]) 
outlier(Cleaned_HDemand) 
grubbs.test(Cleaned_HDemand) # It is not outlier. 
Cleaned_HDemand <- msts(Cleaned_HDemand, seasonal.periods = c(24, 168, 8766),
                        start = c(2005, 1, 1, 1))
class(Cleaned_HDemand)

autoplot(ts_Hourly_Electricity[,1], series="Raw Data") +
  autolayer(Cleaned_HDemand, series="Cleaned Data") +
  ylab("Hourly Electricity") # Only two data points are corrected. 
```

## Hourly Demand 
### Decomposition and Setting training and testing windows
```{r hourly data set decompose, message=FALSE, warning=FALSE}
# Hourly Data Set
# Decompose the time series
Cleaned_HDemand_decompose <- mstl(Cleaned_HDemand)
autoplot(Cleaned_HDemand_decompose)
autoplot(Cleaned_HDemand)
```

```{r daily data set training and testing, message=FALSE, warning=FALSE}
# Create a subset for training purpose
n_forH = 8760 # 365 days x 24 hours 
ts_Cleaned_HDemand_train <- subset(Cleaned_HDemand,
                                   end = length(Cleaned_HDemand)-n_forH)

# Create a subset for testing purpose
ts_Cleaned_HDemand_test <- subset(Cleaned_HDemand,
                                   start = length(Cleaned_HDemand)-n_forH)

autoplot(ts_Cleaned_HDemand_train)
autoplot(ts_Cleaned_HDemand_test)
```

### Generating Time Series Model for Hourly Data Set
#### Model 1: STL + ETS
```{r Hourly Model 1: STL + ETS, message=FALSE, warning=FALSE}
# Fit and forecast STL + ETS model to data
ETS_fitH <-  stlf(ts_Cleaned_HDemand_train, h = 8760)

# Plot foresting results
autoplot(ETS_fitH) + ylab("Hourly Electricity Demand")

# Plot model + observed data
autoplot(ts_Hourly_Electricity[,1]) +
  autolayer(ETS_fitH, series="STL + ETS",PI=FALSE) +
  ylab("Hourly Electricity Demand")

accuracy(ETS_fitH)
```

#### Model 2: ARIMA + FOURIER terms
```{r Hourly Model 2: ARIMA + FOURIER, message=FALSE, warning=FALSE}
# Fit arima model with fourier terms as exogenous regressors
ARIMA_Four_fitH <- auto.arima(ts_Cleaned_HDemand_train, 
                             seasonal=FALSE, 
                             #lambda=0, # It works only after removing lambda=0
                             xreg=fourier(ts_Cleaned_HDemand_train,
                                          K=c(2,12,2)) # Work only after all three terms are identified. 
                             )

ARIMA_Four_forH <- forecast(ARIMA_Four_fitH,
                           xreg=fourier(ts_Cleaned_HDemand_train,
                                        K=c(2,12,2),
                                        h=n_forH),
                           h=n_forH
                           ) 

#Plot foresting results
autoplot(ARIMA_Four_forH) + ylab("Hourly Electricity Demand")

#Plot model + observed data
autoplot(ts_Hourly_Electricity[,1]) +
  autolayer(ARIMA_Four_forH, series="ARIMA_FOURIER",PI=FALSE) +
  ylab("Hourly Electricity Demand")

accuracy(ARIMA_Four_forH)
```

#### Model 3: TBATS
```{r Hourly Model 3: TBATS, message=FALSE, warning=FALSE}
# Fit TBATS Model
TBATS_fitH <- tbats(ts_Cleaned_HDemand_train)

TBATS_forH <- forecast(TBATS_fitH, h=8760)

#Plot foresting results
autoplot(TBATS_forH) +
  ylab("Hourly Electricity Demand") 

#Plot model + observed data
autoplot(ts_Hourly_Electricity[,1]) +
  autolayer(TBATS_forH, series="TBATS",PI=FALSE)+
  ylab("Hourly Electricity Demand") 
```

#### Model 4: Neural Network Time Series Forecasts [2,3]
```{r Daily Model 4: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit23H <- nnetar(ts_Cleaned_HDemand_train,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Cleaned_HDemand_train, K=c(2,12,2)))

NN_for23H <- forecast(NN_fit23H, h=8760,xreg=fourier(ts_Cleaned_HDemand_train, 
                                          K=c(2,12,2),h=8760))


#Plot foresting results
autoplot(NN_for23H) +
  ylab("Hourly Electricity Demand") 

#Plot model + observed data
autoplot(ts_Hourly_Electricity[,1]) +
  autolayer(NN_for23, series="Neural Network 23",PI=FALSE)+
  ylab("Total Electricity Demand") 
```

#### Model 5: Neural Network Time Series Forecasts [2,2]
```{r Daily Model 5: NN, message=FALSE, warning=FALSE}
# Fit NN Model
NN_fit22H <- nnetar(ts_Daily_Electricity_train,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_train, K=c(2,12,2)))

NN_for22H <- forecast(NN_fit22H, h=8760,xreg=fourier(ts_Daily_Electricity_train, 
                                          K=c(2,12,2),h=8760))


#Plot foresting results
autoplot(NN_for22H) +
  ylab("Hourly Electricity Demand") 

#Plot model + observed data
autoplot(ts_Hourly_Electricity[,1]) +
  autolayer(NN_for22H, series="Neural Network 22",PI=FALSE)+
  ylab("Hourly Electricity Demand") 
```

#### Exogenous Variables 
```{r VIF test}
# Correlation Test 
cor.test(Hourly_Electricity$Hourly_demand, Hourly_Electricity$Daily_temp) # Weak negative correlation
cor.test(Hourly_Electricity$Hourly_demand, Hourly_Electricity$Daily_humidity) # Weak negative correlation 
cor.test(Hourly_Electricity$Hourly_temp, Hourly_Electricity$Daily_humidity) # Moderate positive correlation 

# VIF Test
LM_modelH <- lm(Hourly_demand ~ Hourly_temp + Hourly_humidity, data = Hourly_Electricity)
summary(LM_modelH)

vif(LM_modelH) # Test scores less than the standard threshold 5 (Hence, Low Multi-collinearity) 
```

## Accuracy and Performance Testing
```{r hourly model accuracy and performance, warning=FALSE, message=FALSE}
# Model 1: STL + ETS
ETS_scoresH <- accuracy(ETS_fitH$mean,ts_Cleaned_HDemand_test)  

# Model 2: ARIMA + Fourier 
ARIMA_scoresH <- accuracy(ARIMA_Four_forH$mean,ts_Cleaned_HDemand_test)

# Model 3:  TBATS 
TBATS_scores <- accuracy(TBATS_forH$mean,ts_Cleaned_HDemand_test)

# Model 4:  Neural Network 23
NN_scores23H <- accuracy(NN_for23H$mean,ts_Cleaned_HDemand_test)

# Model 5:  Neural Network 22
NN_scores22H <- accuracy(NN_for22H$mean,ts_Cleaned_HDemand_test)

# Create data frame
scoresH <- as.data.frame(
  rbind(ETS_scoresH, ARIMA_scoresH, TBATS_scoresH, NN_scores23H, NN_scores22H)
  )
row.names(scoresH) <- c("STL+ETS", "ARIMA+Fourier","TBATS","NN23", "NN22")

# Choose model with lowest MAPE
best_model_indexH <- which.min(scoresH[,"MAPE"])
cat("The best model by MAPE is:", row.names(scoresH[best_model_index,])) 

# Construct tables
kbl(scores, 
      caption = "Forecast Accuracy for Daily Total Electricity Demand",
      digits = array(5,ncol(scoresH))) %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = "hold_position") %>%
  kable_styling(latex_options="striped", stripe_index = which.min(scores[,"MAPE"]))

# Plot 
autoplot(ts_Hourly_Electricity[,1]) +
  autolayer(ETS_fitH, PI=FALSE, series="STL+ETS") +
  autolayer(ARIMA_Four_forH, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(TBATS_forH,PI=FALSE, series="TBATS") +
  autolayer(NN_for23H,PI=FALSE, series="NN23") +
  autolayer(NN_for22H,PI=FALSE, series="NN22") +
  xlab("Day") + ylab("Hourly Electricity Demand") +
  guides(colour=guide_legend(title="Forecast"))

autoplot(ts_Daily_Electricity_test) +
  autolayer(ETS_fitH, PI=FALSE, series="STL+ETS") +
  autolayer(ARIMA_Four_forH, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(TBATS_forH,PI=FALSE, series="TBATS") +
  autolayer(NN_for23H,PI=FALSE, series="NN") +
  autolayer(NN_for22H,PI=FALSE, series="NN22") +
  ylab("Hourly Electricity Demand") +
  guides(colour=guide_legend(title="Forecast"))
```

## Forecasting for 2011 with fulltrain data set
```{r create full train time series, message=FALSE, warning=}
# Create the time series to retain full data set
ts_Hourly_Electricity_fulltrain <- Cleaned_HDemand
```

### Model 1: STL + ETS
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained STL+ETS Model 
ETS_fit_fulltrainH <- stlf(ts_Hourly_Electricity_fulltrain, h = 1416) # 59 Days x 24 Hours 

# Plot foresting results
autoplot(ETS_fit_fulltrainH) +
  ylab("Hourly Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ETS_fit_fulltrain, series="STL + ETS Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ETS_forecast <- as.data.frame(ETS_fit_fulltrain$mean) %>%
  rename(load = 1) %>%  
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%  
  select(date, load)

# Save forecast in the output folder 
write.csv(ETS_forecast, "Output/ETS_forecast.csv", row.names = FALSE)
```

### Model 2: ARIMA + FOURIER terms
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained ARIMA + Fourier terms Model 
ARIMA_Four_fit_fulltrain <- auto.arima(ts_Daily_Electricity_fulltrain, 
                                       seasonal=FALSE, 
                                       lambda=0,
                                       xreg=fourier(ts_Daily_Electricity_fulltrain,
                                                    K=c(2,3)) 
                                       )

ARIMA_Four_for_fulltrain <- forecast(ARIMA_Four_fit_fulltrain,
                                     xreg=fourier(ts_Daily_Electricity_fulltrain,
                                                  K=c(2,3),
                                                  h=59),
                                     h=59
                                     )

# Plot foresting results
autoplot(ARIMA_Four_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Four_for_fulltrain, series="ARIMA + Fourier Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ARIMA_Four_forecast <- as.data.frame(ARIMA_Four_for_fulltrain$mean) %>%
  rename(load = 1) %>% 
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(ARIMA_Four_forecast, "Output/ARIMA_Four_forecast.csv", row.names = FALSE)
```

### Model 3: TBATS
``` {r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained TBATS Model 
TBATS_fit_fulltrain <- tbats(ts_Daily_Electricity_fulltrain)

TBATS_for_fulltrain <- forecast(TBATS_fit_fulltrain, h=59)
  
# Plot foresting results
autoplot(TBATS_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(TBATS_for_fulltrain, series="TBATS Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
TBATS_Four_forecast <- as.data.frame(TBATS_for_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder
write.csv(TBATS_Four_forecast, "Output/TBATS_Four_forecast.csv", row.names = FALSE)

```

### Model 4: Neural Network [2,3]
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 23 
NN_fit23_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,3)))

NN_for23_fulltrain <- forecast(NN_fit23_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,3),h=59))

# Plot foresting results
autoplot(NN_for23_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for23_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast23 <- as.data.frame(NN_for23_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast23, "Output/NN_forecast23.csv", row.names = FALSE)

```

### Model 5: Neural Network [2,2]
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
## Fit and Forecast the full trained Neural Model 22
NN_fit22_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                 p=1,
                 P=0,
                 xreg=fourier(ts_Daily_Electricity_fulltrain, K=c(2,2)))

NN_for22_fulltrain <- forecast(NN_fit22_fulltrain, h=59,xreg=fourier(ts_Daily_Electricity_fulltrain, 
                                          K=c(2,2),h=59))

# Plot foresting results
autoplot(NN_for22_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NN_for22_fulltrain, series="Neural Network Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NN_forecast22 <- as.data.frame(NN_for22_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NN_forecast22, "Output/NN_forecast22.csv", row.names = FALSE)
```

### Model 6: ARIMA + FOURIER terms + Exo 
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_full <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3))
temp_full <- as.numeric(Daily_Electricity$Daily_temp)
humidity_full <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_combinedfull <- cbind(fourier_full, temp = temp_full, humidity = humidity_full)

# Generate Fourier + exogenous variables for forecasting
fourier_forfull <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 3), h = 59)
temp_forfull <- as.numeric(Daily_Electricity$Daily_temp)
humidity_forfull <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_combined_forfull <- cbind(fourier_forfull, temp = temp_forfull, humidity = humidity_forfull)

# Match column names
colnames(fourier_combined_forfull) <- colnames(fourier_combinedfull)

# Fit and Forecast Model
ARIMA_Fourexo_fit_fulltrain <- auto.arima(ts_Daily_Electricity_fulltrain, 
                                 seasonal = FALSE, 
                                 lambda = 0,
                                 xreg = fourier_combinedfull)

ARIMA_Fourexo_for_fulltrain <- forecast(ARIMA_Fourexo_fit_fulltrain,
                               xreg = fourier_combined_forfull,
                               h = 59)

# Plot foresting results
autoplot(ARIMA_Fourexo_for_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(ARIMA_Fourexo_for_fulltrain, series="ARIMA + Fourier + Exo Model Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
ARIMA_Fourexo_forecast <- as.data.frame(ARIMA_Fourexo_for_fulltrain$mean) %>%
  rename(load = 1) %>% 
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(ARIMA_Fourexo_forecast, "Output/ARIMA_Fourexo_forecast.csv", row.names = FALSE)
```

### Model 7: Neural Network [2,2] + Exo
```{r daily forecast for 2011, message=FALSE, warning=FALSE}
# Generate Fourier + exogenous variables for model fitting
fourier_nnfull <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 2))
temp_nnfull <- as.numeric(Daily_Electricity$Daily_temp)
humidity_nnfull <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_nncombinedfull <- cbind(fourier_nnfull, temp = temp_nnfull, humidity = humidity_nnfull)

# Generate Fourier + exogenous variables for forecasting
fourier_nnforfull <- fourier(ts_Daily_Electricity_fulltrain, K = c(2, 2), h = 59)
temp_nnforfull <- as.numeric(Daily_Electricity$Daily_temp)
humidity_nnforfull <- as.numeric(Daily_Electricity$Daily_humidity)
fourier_combined_nnforfull <- cbind(fourier_nnforfull, temp = temp_nnforfull, humidity = humidity_nnforfull)
# Match column names between training and forecast xreg
colnames(fourier_combined_nnforfull) <- colnames(fourier_nncombinedfull)

# Fit and Forecast the model 
NNexo_fit22_fulltrain <- nnetar(ts_Daily_Electricity_fulltrain,
                      p = 1,
                      P = 0,
                      xreg = fourier_nncombinedfull)

NNexo_for22_fulltrain <- forecast(NNexo_fit22_fulltrain,
                        h = 59,
                        xreg = fourier_combined_nnforfull)

# Plot foresting results
autoplot(NNexo_for22_fulltrain) +
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Plot model + observed data
autoplot(ts_Daily_Electricity[,1]) +
  autolayer(NNexo_for22_fulltrain, series="Neural Network [22] + Exo Full Train",PI=FALSE)+
  ylab("Total Electricity Demand for Jan to Feb 2011") 

# Save forecast values in the data file
NNexo_forecast22 <- as.data.frame(NNexo_for22_fulltrain$mean) %>%
  rename(load = 1) %>%
  mutate(date = seq.Date(from = as.Date("2011-01-01"), 
                         by = "day", 
                         length.out = 59),
         load = round(load)) %>%
  select(date, load)

# Save forecast in the output folder 
write.csv(NNexo_forecast22, "Output/NNexo_forecast22.csv", row.names = FALSE)
```


